---
title: "CONSIGN: GAIA Curation. Part IV"
author: "Francisco Sanchez-Saez"
date: "last-modified" 
editor: source
format:
  html:
    toc: true
    toc-location: left
    theme: cerulean
    css: style.css
    embed-resources: true
    number-sections: true
---

```{r}
#| echo: false
source("_common.R")
knitr::opts_chunk$set(
  eval = FALSE
)

```

```{r }
#| eval: true
#| include: false
# load libraries and functions------------------------------------------------
source(file.path("..", "scripts", "Librerias.R"))
source(file.path("..", "scripts", "Funciones.R"))

```

```{css, echo = FALSE}
.output {
max-height: 500px;
overflow-y: scroll;
}
```

# Load and clean bases

```{r}
# load pathes-----------------------------------------------------------------
path_origenes_consign <- file.path( "F:", "CERES2", "CONSIGN_SD2270", 
                                    "1-DATOS", "1-BRUTOS")

procesados <- file.path( "F:", "CERES2", "CONSIGN_SD2270", 
                         "1-DATOS", "3-PROCESADOS")

```

```{r}
# V3
gaia_v3_cleaned <- fread(file.path("Origin_tables", "auxiliar", 
                                   "gaia_v3_cleaned.csv"),
                         encoding = "Latin-1")

```

# Create tipo_codigo variable

```{r}
# check duplicates-----------------------------------------------------------
gaia_1 <- gaia_v3_cleaned |>
  tidylog::distinct()

rm(gaia_v3_cleaned)

```


```{r}
# types of codes-------------------------------------------------------------
# -1 & -2
sin_referencia <- c("", "-1", "-2", "-1.0", "-2.0")

codigos_gaia <- gaia_1 |>
  distinct(diag_cod)

```


```{r}
# Detect NANDA
nanda1 <- codigos_gaia |> distinct(diag_cod) |> 
  arrange(diag_cod) |> 
  filter(str_detect(diag_cod, "\\.") == FALSE) |> 
  filter(diag_cod %nin% c("605A", "605B")) |> 
  filter(nchar(diag_cod) > 3) |> 
  filter(str_starts(diag_cod, "E") == FALSE) |> 
  pull(diag_cod)
nanda2 <- codigos_gaia |> distinct(diag_cod) |> 
  arrange(diag_cod) |>
  filter(str_detect(diag_cod, "\\.") == TRUE) |> 
  filter(str_starts(diag_cod, "000") == TRUE) |> 
  pull(diag_cod)
# cie9 without letters 3 digits without point + 605A and 605B
cie9_1 <- codigos_gaia |> distinct(diag_cod) |> 
  arrange(diag_cod) |> 
  filter(nchar(diag_cod) == 3 | diag_cod %in% c("605A", "605B")) |>  
  filter(str_starts(diag_cod, "\\d") == TRUE) |>
  filter(str_detect(diag_cod, "\\.") == FALSE) |>  
  pull(diag_cod)
# cie9 without letters with point
cie9_2 <- codigos_gaia |> distinct(diag_cod) |> 
  arrange(diag_cod) |>
  filter(str_starts(diag_cod, "\\d\\d\\d\\.") == TRUE) |> 
  pull(diag_cod)
# cie9 E
cie9_3 <- codigos_gaia |> distinct(diag_cod) |> 
  arrange(diag_cod) |>
  filter(str_starts(diag_cod, "E\\d\\d\\d\\.") == TRUE) |> 
  pull(diag_cod)
cie9_4 <- codigos_gaia |> distinct(diag_cod) |> 
  arrange(diag_cod) |>
  filter(str_starts(diag_cod, "E\\d\\d\\d") == TRUE) |> 
  filter(nchar(diag_cod) == 4) |> 
  pull(diag_cod)
# cie9 V
cie9_5 <- codigos_gaia |> distinct(diag_cod) |> 
  arrange(diag_cod) |>
  filter(str_starts(diag_cod, "V\\d\\d") == TRUE) |> 
  filter(nchar(diag_cod) == 3) |> 
  pull(diag_cod)
cie9_6 <- codigos_gaia |> distinct(diag_cod) |> 
  arrange(diag_cod) |>
  filter(str_starts(diag_cod, "V\\d\\d\\.\\d") == TRUE) |> 
  filter(nchar(diag_cod) == 5) |> 
  pull(diag_cod)
cie9_7 <- codigos_gaia |> distinct(diag_cod) |> 
  arrange(diag_cod) |>
  filter(str_starts(diag_cod, "V\\d\\d\\.\\d\\d") == TRUE) |> 
  filter(nchar(diag_cod) == 6) |> 
  pull(diag_cod)
cie9_8 <- codigos_gaia |> distinct(diag_cod) |> 
  arrange(diag_cod) |>
  filter(str_starts(diag_cod, "V\\d\\d\\.\\d\\d") == TRUE) |> 
  filter(nchar(diag_cod) == 7) |> 
  pull(diag_cod)
cie9_9 <- codigos_gaia |> distinct(diag_cod) |> 
  arrange(diag_cod) |>
  filter(str_starts(diag_cod, "V76\\.\\d") == TRUE) |> 
  filter(nchar(diag_cod) == 6) |> 
  pull(diag_cod)
# cie10 without E nor V
cie10_1 <- codigos_gaia |> distinct(diag_cod) |> 
  arrange(diag_cod) |>
  filter(str_starts(diag_cod, "V") == FALSE) |>
  filter(str_starts(diag_cod, "E") == FALSE) |>
  filter(str_starts(diag_cod, "\\d") == FALSE) |> 
  filter(diag_cod %nin% sin_referencia) |> 
  filter(str_starts(diag_cod, ".\\d")) |> 
  filter(nchar(diag_cod) == 3) |> 
  pull(diag_cod)
cie10_2 <- codigos_gaia |> distinct(diag_cod) |> 
  arrange(diag_cod) |>
  filter(str_starts(diag_cod, "V") == FALSE) |>
  filter(str_starts(diag_cod, "E") == FALSE) |>
  filter(str_starts(diag_cod, "\\d") == FALSE) |> 
  filter(diag_cod %nin% sin_referencia) |> 
  filter(str_starts(diag_cod, ".\\d.\\.")) |> 
  pull(diag_cod)
# cie10 E
cie10_3 <- codigos_gaia |> distinct(diag_cod) |> 
  arrange(diag_cod) |>
  filter(str_starts(diag_cod, "E\\d\\d") == TRUE) |>
  filter(nchar(diag_cod) == 3) |> 
  pull(diag_cod)
cie10_4 <- codigos_gaia |> distinct(diag_cod) |> 
  arrange(diag_cod) |>
  filter(str_starts(diag_cod, "E\\d\\d\\.") == TRUE) |> 
  pull(diag_cod)
# cie10 V
cie10_5 <- codigos_gaia |> distinct(diag_cod) |> 
  arrange(diag_cod) |>
  filter(str_starts(diag_cod, "V") == TRUE) |>
  filter(nchar(diag_cod) > 7) |> 
  pull(diag_cod)
cie10_6 <- codigos_gaia |> distinct(diag_cod) |> 
  arrange(diag_cod) |>
  filter(str_starts(diag_cod, "V") == TRUE) |>
  filter(str_ends(diag_cod, "X") == TRUE) |>
  pull(diag_cod)

cie9 <- c(cie9_1, cie9_2, cie9_3, cie9_4, cie9_5, cie9_6, cie9_7, cie9_8, cie9_9)
cie10 <- c(cie10_1, cie10_2, cie10_3, cie10_4, cie10_5, cie10_6)
nanda <- c(nanda1, nanda2)

```

```{r}
# create tipo_codigo---------------------------------------------------------
codigos_maestro_gaia_0 <- codigos_gaia |> 
  distinct(diag_cod) |> 
  mutate(tipo_codigo = case_when(
    diag_cod %in% sin_referencia ~ "No ref",
    diag_cod %in% nanda ~ "NANDA",
    diag_cod %in% cie9 ~ "ICD9CM",
    diag_cod %in% cie10 ~ "ICD10ES",
    T ~ "Others"))
  
```

```{r}
# There are not diag_desc so this is unfeasible
# codigos_maestro_gaia_1 <- codigos_maestro_gaia_0 |> 
# # change the "V" codes that are accidents
#   tidylog::mutate(tipo_codigo = if_else(str_starts(diag_cod, "V") == TRUE &
#        str_detect(diag_desc, 
#   "ACCIDENTE|COLISION|QUEMADURA DEBIDA A FUEGO EN OTRA EMBARCACION MOTORIZADA"
#   ) == TRUE, "ICD10ES", tipo_codigo)) |>  
#   # change the "V" codes that are observations
#   tidylog::mutate(tipo_codigo = if_else(str_starts(diag_cod, "V71.") == TRUE & 
#       str_detect(diag_desc, 
#        "OBSERVACION DESPUES DE") == TRUE,
#        "ICD9CM", tipo_codigo)) |>  
#   tidylog::mutate(tipo_codigo = if_else(str_starts(diag_cod, "V07") == TRUE, 
#        "ICD9CM", tipo_codigo)) 


```

```{r}
#check codigos_maestro_gaia_0
codigos_maestro_gaia_0 |> filter(str_starts(diag_cod, "E") == TRUE) |> 
  distinct(diag_cod, tipo_codigo) |> 
   arrange(diag_cod)

codigos_maestro_gaia_0 |> filter(str_starts(diag_cod, "V") == TRUE) |> 
  distinct(diag_cod, tipo_codigo) |> 
   arrange(diag_cod)

```


```{r}
# check codes one by one in the ecieMap`s (codes from aed)
codigos_maestro_gaia_1 <- codigos_maestro_gaia_0 |> 
  tidylog::mutate(tipo_codigo = case_when(
    # discovered during OMOP CDM standardization
    diag_cod == "V03.10X" ~ "ICD10ES",
    diag_cod == "V09.29X" ~ "ICD10ES",
    diag_cod == "V29.49X" ~ "ICD10ES",
    diag_cod == "V43.04X" ~ "ICD10ES",
    diag_cod == "V43.92X" ~ "ICD10ES",
    diag_cod == "V93.19X" ~ "ICD10ES",
    diag_cod == "V00.128" ~ "ICD10ES",
    diag_cod == "V00.131" ~ "ICD10ES",
    diag_cod == "V00.83" ~ "ICD10ES",
    diag_cod == "V00.831" ~ "ICD10ES",
    diag_cod == "V09.20" ~ "ICD10ES",
    diag_cod == "V09.29" ~ "ICD10ES",
    diag_cod == "V43.04" ~ "ICD10ES",
    diag_cod == "V43.92" ~ "ICD10ES",
    diag_cod == "V88.9" ~ "ICD10ES",
    diag_cod == "V89.2" ~ "ICD10ES",
    diag_cod == "V94.8" ~ "ICD10ES",
    diag_cod == "V95.4" ~ "ICD10ES",
    # other ambigous codes
    diag_cod == "V02.51" ~ "ICD9CM",
    diag_cod == "V03.10" ~ "ICD10ES",
    diag_cod == "V08" ~ "ICD9CM",
    # could be both
    # diag_cod == "V10.3" ~ "ICD9CM",
    diag_cod == "V10.87" ~ "ICD9CM",
    # could be both
    # diag_cod == "V12.2" ~ "ICD9CM",
    diag_cod == "V12.59" ~ "ICD9CM",
    diag_cod == "V13.29" ~ "ICD9CM",
    # could be both
    # diag_cod == "V14.1" ~ "ICD9CM",
    diag_cod == "V14.6" ~ "ICD9CM",
    diag_cod == "V14.8" ~ "ICD9CM",
    diag_cod == "V15.08" ~ "ICD9CM",
    diag_cod == "V15.59" ~ "ICD9CM",
    diag_cod == "V15.82" ~ "ICD9CM",
    # could be both
    # diag_cod == "V18.1" ~ "ICD9CM",
    # could be both
    # diag_cod == "V19.5" ~ "ICD9CM",
    # could be both
    # diag_cod == "V22.0" ~ "ICD9CM",
    # could be both
    # diag_cod == "V22.1" ~ "ICD9CM",
    # could be both
    # diag_cod == "V22.2" ~ "ICD9CM",
    diag_cod == "V23.85" ~ "ICD9CM",
    diag_cod == "V23.89" ~ "ICD9CM",
    # could be both
    # diag_cod == "V23.9" ~ "ICD9CM",
    # could be both
    # diag_cod == "V24.0" ~ "ICD9CM",
    # could be both
    # diag_cod == "V24.2" ~ "ICD9CM",
    diag_cod == "V25.42" ~ "ICD9CM",
    diag_cod == "V25.49" ~ "ICD9CM",
    diag_cod == "V28.8" ~ "ICD9CM",
    # could be both
    # diag_cod == "V41.1" ~ "ICD9CM",
    # could be both
    # diag_cod == "V42.0" ~ "ICD9CM",
    diag_cod == "V43.82" ~ "ICD9CM",
    # could be both
    # diag_cod == "V44.6" ~ "ICD9CM",
    diag_cod == "V45.51" ~ "ICD9CM",
    diag_cod == "V45.73" ~ "ICD9CM",
    diag_cod == "V45.77" ~ "ICD9CM",
    diag_cod == "V45.79" ~ "ICD9CM",
    diag_cod == "V45.89" ~ "ICD9CM",
    diag_cod == "V58.11" ~ "ICD9CM",
    diag_cod == "V58.49" ~ "ICD9CM",
    diag_cod == "V58.61" ~ "ICD9CM",
    # could be both
    # diag_cod == "V61.5" ~ "ICD9CM",
    diag_cod == "V62.82" ~ "ICD9CM",
    # could be both
    # diag_cod == "V65.5" ~ "ICD9CM",
    # could be both
    # diag_cod == "V67.9" ~ "ICD9CM",
    diag_cod == "V71.89" ~ "ICD9CM",
    # could be both
    # diag_cod == "V71.9" ~ "ICD9CM",
    # could be both
    # diag_cod == "V72.4" ~ "ICD9CM",
    # could be both
    # diag_cod == "V72.6" ~ "ICD9CM",
    diag_cod == "V78.8" ~ "ICD9CM",
    diag_cod == "V87.9XX" ~ "ICD10ES",
    T ~ tipo_codigo
  )) |> 
  tidylog::distinct()

```
```{r}
# check codes
codigos_maestro_gaia_1 |> count(tipo_codigo)

```

# Fix incorrect ICD codes 

During the ETL process for the OMOP CDM, we have encountered incorrect ICD9CM and ICD10ES codes that lack an associated standard_concept_id. In this section, we address and rectify these code issues. 

```{r}
# load concepts vocabulary---------------------------------------------------
concepts_vocabulary <- fread(file.path("..", "EHDEN", 
                                       "Vocabularies", "concept.csv"))

```


Typically, there are two types of issues:

**1. Addition of a letter or letters at the end of the code:** In certain cases, as a result of Spanish (or regional) adaptation of the ICD standards, one or more letters are appended at the end of the code to indicate a specification (e.g., 413.9A, S30.1X). To resolve this issue, we remove the extraneous letter (e.g., 413.9, S30.1).

**2. Presence of extra digits:** Some codes contain additional digits (e.g., 645.0 or 715.99), which we assume to be errors. To correct this, we remove the extra digits, resulting in revised codes (e.g., 645 or 715.9).

By addressing these issues, we ensure the accuracy and consistency of the ICD9CM and ICD10ES (ICD10CM) codes within the OMOP CDM.

## Correct ICD9CM codes

```{r}
# obtain icd9 concepts vocabulary--------------------------------------------
icd9_concepts <- concepts_vocabulary |> 
  filter(vocabulary_id == "ICD9CM")

```

```{r}
# gaia codes------------------------------------------------------------------
map_gaia_icd9_to_concept_id_0 <- codigos_maestro_gaia_1 |>
  filter(tipo_codigo == "ICD9CM") |> 
  distinct(diag_cod) |> 
  arrange(diag_cod)  |> 
  left_join(icd9_concepts, by = c("diag_cod" = "concept_code"))

# check
wrong_gaia_icd9_codes <- map_gaia_icd9_to_concept_id_0 |>
  select(diag_cod, concept_id) |> 
  filter(is.na(concept_id)) |>
  select(-concept_id) |> 
  mutate(.before = 1, issue = if_else(str_detect(diag_cod, "\\d[aA-zZ]"), 
                         "letter at the end", "non-existent code")) |> 
  arrange(issue, diag_cod)

```

```{r}
# fix the unmapped codes-----------------------------------------------------
wrong_gaia_icd9_codes_corrected <- wrong_gaia_icd9_codes |> 
  mutate(diag_cod_cleaned = case_when(
  # remove the last letter for CV specification
  str_detect(diag_cod, "\\d[aA-zZ]") == TRUE ~ 
    str_sub(diag_cod, 1, nchar(diag_cod) - 1),
  # correct errors
  diag_cod == "712.0"  ~ "712",
  diag_cod == "715.99" ~ "715.9",
  T ~ diag_cod
    ))

saveRDS(wrong_gaia_icd9_codes_corrected, file.path("Resultados", "icd_issues",
                               "wrong_gaia_icd9_codes_corrected.RDS"))

```

<br>

```{r}
#| eval: true
#| echo: false
#| tbl-cap-location: top
#| tbl-cap: "ICD9CM Code Issues in GAIA Table"
#| label: tbl-gaiaicd9issues

# table of the wrong codes and the proposed fix------------------------------
wrong_gaia_icd9_codes_corrected <- readRDS(file.path("Resultados", "icd_issues",
                               "wrong_gaia_icd9_codes_corrected.RDS"))

wrong_gaia_icd9_codes_corrected |>
  gt(id = "gaiaicd9") |>  # need to name the table to apply CSS
  fmt_markdown(columns = everything()) |> 
  cols_label(issue = "Issue",
             diag_cod = "Original code",
             diag_cod_cleaned = "Corrected code"
             )|> 
  tab_style(
    style = list(
      cell_fill(color = "#9473d8"),
      cell_text(color = "white", align = "center", weight = "bold")
    ),
    locations = cells_column_labels()) |>
  cols_align(
  align = "center",
  columns = everything()) |> 
    opt_row_striping( row_striping = TRUE) |>
  tab_options(
    container.height = "400px"
  ) |>  
  opt_css(
    css = "
    #gaiaicd9 tr:hover {
    background-color: #f2cce4;
    }
    ")

```

<br>

```{r}
# fix the unmapped codes in the gaia table------------------------------------
codigos_maestro_gaia_2 <- codigos_maestro_gaia_1 |> 
  left_join(wrong_gaia_icd9_codes_corrected |> 
              mutate(tipo_codigo = "ICD9CM")) |>
  select(-issue) |> 
  tidylog::distinct()

```


```{r}
# map again with the corrected codes-----------------------------------------
map_gaia_icd9_to_concept_id <- codigos_maestro_gaia_2 |>
  filter(tipo_codigo == "ICD9CM") |>
  mutate(diag_cod = if_else(!is.na(diag_cod_cleaned),
                            diag_cod_cleaned, diag_cod)) |> 
  select(-diag_cod_cleaned) |>
  distinct(diag_cod) |> 
  arrange(diag_cod) |> 
  left_join(icd9_concepts, by = c("diag_cod" = "concept_code"))

# check
map_gaia_icd9_to_concept_id |>
  select(diag_cod, concept_id) |> 
  filter(is.na(concept_id))
## all is mapped -> OK

```

## Correct ICD10ES codes

```{r}
# obtain icd9 concepts vocabulary--------------------------------------------
icd10_concepts <- concepts_vocabulary |> 
  filter(vocabulary_id == "ICD10CM")

```

```{r}
# gaia codes------------------------------------------------------------------
map_gaia_icd10_to_concept_id_0 <- codigos_maestro_gaia_2 |>
  filter(tipo_codigo == "ICD10ES") |> 
  distinct(diag_cod) |> 
  arrange(diag_cod)  |> 
  left_join(icd10_concepts, by = c("diag_cod" = "concept_code"))

# check
wrong_gaia_icd10_codes <- map_gaia_icd10_to_concept_id_0 |>
  select(diag_cod, concept_id) |> 
  filter(is.na(concept_id)) |>
  select(-concept_id) |> 
  mutate(.before = 1, issue = if_else(str_detect(diag_cod, "\\d?[aA-zZ]"), 
                         "letter at the end", "non-existent code")) |> 
  arrange(issue, diag_cod)

```


```{r}
# check the fix
codigos_maestro_gaia_2 |>
  filter(tipo_codigo == "ICD10ES") |> 
  distinct(diag_cod) |>
  filter(diag_cod %in% (wrong_gaia_icd10_codes |> pull(diag_cod))) |> 
  arrange(diag_cod) |> 
  mutate(diag_cod_cleaned = str_remove(diag_cod, "(X{1,3}|\\.[X]{1,3})$")) |> 
  tidylog::distinct()

# the fix is correct

```


```{r}
# fix the unmapped codes-----------------------------------------------------
wrong_gaia_icd10_codes_corrected <- wrong_gaia_icd10_codes |> 
  mutate(diag_cod_cleaned = str_remove(diag_cod, "(X{1,3}|\\.[X]{1,3})$"))

saveRDS(wrong_gaia_icd10_codes_corrected, file.path("Resultados", "icd_issues",
                               "wrong_gaia_icd10_codes_corrected.RDS"))

```

<br>

```{r}
#| eval: true
#| echo: false
#| tbl-cap-location: top
#| tbl-cap: "ICD10CM Code Issues in gaia Table"
#| label: tbl-gaiaicd10issues

# table of the wrong codes and the proposed fix------------------------------
wrong_gaia_icd10_codes_corrected <- readRDS(file.path("Resultados", "icd_issues",
                               "wrong_gaia_icd10_codes_corrected.RDS"))

wrong_gaia_icd10_codes_corrected |>
  gt(id = "gaiaicd10") |>  # need to name the table to apply CSS
  fmt_markdown(columns = everything()) |> 
  cols_label(issue = "Issue",
             diag_cod = "Original code",
             diag_cod_cleaned = "Corrected code"
             )|> 
  tab_style(
    style = list(
      cell_fill(color = "#9473d8"),
      cell_text(color = "white", align = "center", weight = "bold")
    ),
    locations = cells_column_labels()) |>
  cols_align(
  align = "center",
  columns = everything()) |> 
    opt_row_striping( row_striping = TRUE) |>
  tab_options(
    container.height = "400px"
  ) |>  
  opt_css(
    css = "
    #gaiaicd10 tr:hover {
    background-color: #f2cce4;
    }
    ")

```

::: {.callout-important}
There are not ICD10ES issues in the **GAIA** table.
:::

<br>

```{r}
# fix the unmapped codes in the gaia table-----------------------------------
codigos_maestro_gaia_3 <- codigos_maestro_gaia_2 |> 
  left_join(wrong_gaia_icd10_codes_corrected |> 
              mutate(tipo_codigo = "ICD10ES"), 
            by = c("diag_cod", "tipo_codigo")) |>
  tidylog::distinct() |> 
  mutate(diag_cod_cleaned = if_else(
    !is.na(diag_cod_cleaned.x), diag_cod_cleaned.x, diag_cod_cleaned.y)) |> 
  select(-diag_cod_cleaned.x, -diag_cod_cleaned.y, -issue)

```


```{r}
# map again with the corrected codes-----------------------------------------
map_gaia_icd10_to_concept_id <- codigos_maestro_gaia_3 |>
  filter(tipo_codigo == "ICD10ES") |>
  mutate(diag_cod = if_else(!is.na(diag_cod_cleaned),
                            diag_cod_cleaned, diag_cod)) |>
  select(-diag_cod_cleaned) |> 
  arrange(diag_cod) |> 
  left_join(icd10_concepts, by = c("diag_cod" = "concept_code"))

# check
map_gaia_icd10_to_concept_id |>
  select(diag_cod, concept_id) |> 
  filter(is.na(concept_id))
## all is mapped -> OK

```

# Include tipo_codigo into GAIA

```{r}
# add tipo_codigo and corrected codes----------------------------------------
gaia_2 <- gaia_1 |> 
  # add tipo_codigo1
  left_join(codigos_maestro_gaia_3, 
            by = c("diag_cod" = "diag_cod")) |>
  mutate(diag_cod = if_else(!is.na(diag_cod_cleaned),
                            diag_cod_cleaned, diag_cod)) 
# check
gaia_2 |> count(tipo_codigo)

```

# Fix bases with the feedback from the Quality Checks

Note that we are using the *tidylog* variation of *tidyverse* verbs in order to obtain more information about the curation process.

```{r}
# fix base-------------------------------------------------------------------
gaia_3 <- gaia_2 |>
# rename and select variables to fit with the excel (make the changes at the beginning)
  mutate(f_fact = f_disp) |>
  mutate(tipo_receta = case_when(
    is.na(f_fact) ~ 1,
    is.na(f_pres) ~ 2,
    TRUE ~ 3
  )) |>
  mutate(fecha_receta = if_else(!is.na(f_pres), f_pres, f_disp)) |> 
  select(
    sip = sip,
    receta_id = id_receta,
    tx_id = id_trat,
    fecha_pres = f_pres,
    fecha_fact = f_fact,
    fecha_disp = f_disp,
    fecha_ini_trat = fecha_ini_trat,
    fecha_fin_trat = fecha_fin_trat,
    atc_cod = atc_cod,
    atc_desc = atc_desc,
    prin_act_cod = prin_act_cod,
    prin_act_desc = prin_act_desc,
    pres_farma_cod = pres_farma_cod,
    pres_farma_desc = pres_farma_desc,
    via_cod = via_cod,
    via_desc = via_desc,
    precio = precio,
    estado_receta = estado_receta,
    elec_manu = receta_abucasis,
    unidades = unidades,
    cadencia = cadencia,
    estado_tx = estado_trat,
    env_durac = env_durac,
    diag_cod = diag_cod,
    tipo_codigo = tipo_codigo,
    tipo_receta = tipo_receta, 
    fecha_receta = fecha_receta,
    duracion_receta = env_durac,
    duracion_composite = env_durac
  )

```

```{r}
# depure base from QC feedback-----------------------------------------------
gaia_non_standard <- gaia_3 |> 
  # select CONSIGN study period
  tidylog::filter(fecha_receta <= ymd("2021-12-31")) |> 
  # remove missing sip (RFqwh4PcfAcSBlICoKtN/w==)
  tidylog::filter(sip != "RFqwh4PcfAcSBlICoKtN/w==") |>
  # check duplicates
  tidylog::distinct()

# check gaia dates
gaia_non_standard |> skim(fecha_receta, fecha_pres, fecha_disp, fecha_fact)

```

```{r}
# create master of clinical drugs--------------------------------------------
gaia_clinical_drugs <- gaia_non_standard |> distinct(
  pres_farma_cod,
  pres_farma_desc,
  atc_cod,
  atc_desc,
  prin_act_cod,
  prin_act_desc,
  via_cod,
  via_desc
)

# save master----------------------------------------------------------------
fwrite(gaia_clinical_drugs, file.path("Resultados", "gaia_masters",
                                      "gaia_clinical_drugs.csv"))

```

# Save base

```{r}
# save gaia------------------------------------------------------------------

# save in SSD
fwrite(gaia_non_standard, append = FALSE, 
       file = file.path("Origin_tables", "auxiliar",
                "gaia_non_standard.csv"))

```

```{r}
#| include: false
# copy .qmd to CERES---------------------------------------------------------
unlink(file.path("F:", "CERES2", "CONSIGN_SD2270", "2-SCRIPTS", "R",
                 "1_07_4_GAIA_tipo_codigo_CONSIGN.qmd"))
file.copy(from = file.path("1_07_4_GAIA_tipo_codigo_CONSIGN.qmd"),
          to = file.path("F:", "CERES2", "CONSIGN_SD2270",
                         "2-SCRIPTS", "R"))

```

<div class="tocify-extend-page" data-unique="tocify-extend-page" style="height: 0;"></div>
