---
title: "CONSIGN: GAIA Curation. Part V"
author: "Francisco Sanchez-Saez"
date: "last-modified" 
editor: source
format:
  html:
    toc: true
    toc-location: left
    theme: cerulean
    css: style.css
    embed-resources: true
    number-sections: true
---

```{r}
#| echo: false
source("_common.R")
knitr::opts_chunk$set(
  eval = FALSE
)

```

```{r }
#| eval: true
#| include: false
# load libraries and functions------------------------------------------------
source(file.path("..", "scripts", "Librerias.R"))
source(file.path("..", "scripts", "Funciones.R"))

```

```{css, echo = FALSE}
.output {
max-height: 500px;
overflow-y: scroll;
}
```

# Load and clean bases

```{r}
# load pathes----------------------------------------------------------------
path_origenes_consign <- file.path( "F:", "CERES2", "CONSIGN_SD2270", 
                                    "1-DATOS", "1-BRUTOS")

procesados <- file.path( "F:", "CERES2", "CONSIGN_SD2270", 
                         "1-DATOS", "3-PROCESADOS")

```

```{r}
# load gaia------------------------------------------------------------------
gaia_clinical_drugs <- fread(file.path("Resultados", "gaia_masters",
                                      "gaia_clinical_drugs.csv"),
                             encoding = "Latin-1")

```

```{r}
# load concepts vocabulary---------------------------------------------------
concepts_vocabulary <- fread(file.path("..", "EHDEN",
  "Vocabularies", "CONCEPT.csv"))
concepts_relationship <- fread(file.path("..", "EHDEN",
  "Vocabularies", "CONCEPT_RELATIONSHIP.csv"))
concepts_ancestor <- fread(file.path("..", "EHDEN",
  "Vocabularies", "CONCEPT_ANCESTOR.csv"))

```

```{r}
# check multiple descriptions------------------------------------------------
gaia_clinical_drugs |> 
  add_count(pres_farma_cod) |> 
  filter(n > 1)

```

# Fix formas and nformas

```{r}
# fix "forma" and "nforma"---------------------------------------------------
pres_farma_master <- gaia_clinical_drugs |> distinct(
  pres_farma_cod,
  pres_farma_desc)

pres_farma_master2 <- pres_farma_master |> 
  mutate(
  texto_forma = str_split_fixed(pres_farma_desc,
  pattern = " / ", n = 2)[,2],
# extract first number and word after the "/"--------------------------------------
  nforma = str_split(texto_forma, pattern = " ", simplify = TRUE, n = 3)[, 1],
  forma = str_split(texto_forma, pattern = " ", simplify = TRUE, n = 3)[, 2])

```

## Fix nformas

```{r}
# fix errors in nforma-------------------------------------------------------
raw_nformas <- pres_farma_master2 |> distinct(nforma) |> 
  arrange(nforma) |> pull()

```


```{r}
# fix nforma = ""------------------------------------------------------------
pres_farma_master2 |> filter(nforma == raw_nformas[1]) |> 
  arrange(pres_farma_cod)

pres_farma_master3 <- pres_farma_master2 |> 
  mutate(nforma = case_when(
    pres_farma_cod == 2740 ~ "28",
    pres_farma_cod == 5799 ~ "5",
    pres_farma_cod == 7807 ~ "1",
    pres_farma_cod == 8837 ~ "2",
    pres_farma_cod == 9373 ~ "28",
    pres_farma_cod == 10213 ~ "30",
    pres_farma_cod == 10365 ~ "1",
    pres_farma_cod == 10923 ~ "40",
    pres_farma_cod == 11085 ~ "10",
    pres_farma_cod == 11316 ~ "1",
    pres_farma_cod == 11399 ~ "1",
    pres_farma_cod == 11431 ~ "1",
    pres_farma_cod == 11448 ~ "1",
    pres_farma_cod == 11555 ~ "1",
    pres_farma_cod == 12219 ~ "1",
    pres_farma_cod == 12272 ~ "30",
    pres_farma_cod == 12273 ~ "60",
    pres_farma_cod == 12787 ~ "5",
    pres_farma_cod == 12790 ~ "5",
    pres_farma_cod == 13010 ~ "1",
    pres_farma_cod == 14155 ~ "30",
    pres_farma_cod == 15923 ~ "1",
    pres_farma_cod == 16262 ~ "1",
    pres_farma_cod == 16506 ~ "20",
    pres_farma_cod == 16870 ~ "1",
    pres_farma_cod == 17080 ~ "1",
    pres_farma_cod == 17171 ~ NA_character_,
    pres_farma_cod == 17936 ~ "6",
    pres_farma_cod == 17938 ~ "6",
    pres_farma_cod == 18480 ~ "1",
    pres_farma_cod == 23524 ~ "1",
    pres_farma_cod == 23670 ~ NA_character_,
    pres_farma_cod == 23723 ~ "1",
    pres_farma_cod == 24103 ~ NA_character_,
    pres_farma_cod == 24439 ~ NA_character_,
    pres_farma_cod == 24473 ~ NA_character_,
    pres_farma_cod == 24696 ~ "1",
    pres_farma_cod == 25085 ~ NA_character_,
    pres_farma_cod == 25143 ~ NA_character_,
    pres_farma_cod == 25153 ~ NA_character_,
    pres_farma_cod == 25459 ~ "1",
    pres_farma_cod == 25584 ~ NA_character_,
    pres_farma_cod == 25599 ~ NA_character_,
    pres_farma_cod == 25704 ~ NA_character_,
    pres_farma_cod == 25722 ~ "1",
    pres_farma_cod == 25723 ~ "1",
    pres_farma_cod == 26281 ~ NA_character_,
    pres_farma_cod == 26356 ~ NA_character_,
    pres_farma_cod == 26443 ~ "1",
    pres_farma_cod == 26573 ~ "1",
    pres_farma_cod == 27528 ~ NA_character_,
    pres_farma_cod == 27529 ~ NA_character_,
    pres_farma_cod == 27807 ~ NA_character_,
    pres_farma_cod == 27834 ~ NA_character_,
    pres_farma_cod == 27894 ~ NA_character_,
    pres_farma_cod == 28120 ~ "1",
    pres_farma_cod == 28755 ~ NA_character_,
      T ~ nforma
  )) |> 
  mutate(forma = case_when(
    pres_farma_cod == 2740 ~ "CAPSULAS LIBERACION RETARDADA",
    pres_farma_cod == 5799 ~ "PARCHE TRANSDERMICO",
    pres_farma_cod == 7807 ~ "SOLUCION",
    pres_farma_cod == 8837 ~ "PULVERIZADOR",
    pres_farma_cod == 9373 ~ "COMPRIMIDOS RECUBIERTOS",
    pres_farma_cod == 10213 ~ "JERINGA",
    pres_farma_cod == 10365 ~ "VIAL",
    pres_farma_cod == 10923 ~ "COMPRIMIDOS RECUBIERTOS",
    pres_farma_cod == 11085 ~ "COMPRIMIDOS",
    pres_farma_cod == 11316 ~ "SOLUCION",
    pres_farma_cod == 11399 ~ "SPRAY",
    pres_farma_cod == 11431 ~ "SOLUCION",
    pres_farma_cod == 11448 ~ "JARABE",
    pres_farma_cod == 11555 ~ "VIAL + JERINGA",
    pres_farma_cod == 12219 ~ "SPRAY NASAL",
    pres_farma_cod == 12272 ~ "CAPSULAS",
    pres_farma_cod == 12273 ~ "CAPSULAS",
    pres_farma_cod == 12787 ~ "CARTUCHO/PLUMA",
    pres_farma_cod == 12790 ~ "CARTUCHO/PLUMA",
    pres_farma_cod == 13010 ~ "SOLUCION GOTAS",
    pres_farma_cod == 14155 ~ "COMPRIMIDOS SUBLINGUALES",
    pres_farma_cod == 15923 ~ "SOLUCION",
    pres_farma_cod == 16262 ~ "GOTAS NASALES",
    pres_farma_cod == 16506 ~ "SOBRES",
    pres_farma_cod == 16870 ~ "GRANULADO PARA SUSPENSION ORAL",
    pres_farma_cod == 17080 ~ "SOLUCION PARA PULVERIZACION NASAL",
    pres_farma_cod == 17171 ~ "CAPSULAS",
    pres_farma_cod == 17936 ~ "SOLUCION PARA PULVERIZACION NASAL",
    pres_farma_cod == 17938 ~ "SOLUCION PARA PULVERIZACION NASAL",
    pres_farma_cod == 18480 ~ "SOLUCION",
    pres_farma_cod == 23524 ~ "SOLUCION",
    pres_farma_cod == 23670 ~ "CAPSULAS",
    pres_farma_cod == 23723 ~ "JERINGA",
    pres_farma_cod == 24103 ~ "CAPSULAS",
    pres_farma_cod == 24439 ~ "CAPSULAS",
    pres_farma_cod == 24473 ~ "CAPSULAS",
    pres_farma_cod == 24696 ~ "SUSPENSION",
    pres_farma_cod == 25085 ~ "SOBRES",
    pres_farma_cod == 25143 ~ "CAPSULAS",
    pres_farma_cod == 25153 ~ "CAPSULAS",
    pres_farma_cod == 25459 ~ "SUSPENSION",
    pres_farma_cod == 25584 ~ "CAPSULAS",
    pres_farma_cod == 25599 ~ "CAPSULAS",
    pres_farma_cod == 25704 ~ "CAPSULAS",
    pres_farma_cod == 25722 ~ "INHALADOR",
    pres_farma_cod == 25723 ~ "INHALADOR",
    pres_farma_cod == 26281 ~ "CAPSULAS",
    pres_farma_cod == 26356 ~ "CAPSULAS",
    pres_farma_cod == 26443 ~ "SUSPENSION",
    pres_farma_cod == 26573 ~ "PLUMA PREGARGADA",
    pres_farma_cod == 27528 ~ "CAPSULAS",
    pres_farma_cod == 27529 ~ "CAPSULAS",
    pres_farma_cod == 27807 ~ "SOBRES",
    pres_farma_cod == 27834 ~ "SOBRES",
    pres_farma_cod == 27894 ~ "SOBRES",
    pres_farma_cod == 28120 ~ "INHALADOR",
    pres_farma_cod == 28755 ~ "SOBRES",
    T ~ forma
  ))

# check correction
pres_farma_master3 |> filter(nforma == raw_nformas[1])

```

```{r}
# fix nforma = "(xxMG/xxMG)"--------------------------------------------------
pres_farma_master3 |> filter(nforma %in% c(raw_nformas[2], raw_nformas[3])) |> 
  arrange(pres_farma_cod)

pres_farma_master4 <- pres_farma_master3 |> 
  mutate(nforma = case_when(
    pres_farma_cod == 16326 ~ "1",
    pres_farma_cod == 16433 ~ "1",
    T ~ nforma)) |>
  mutate(forma = case_when(
    pres_farma_cod == 16326 ~ "VIAL + JERINGA",
    pres_farma_cod == 16433 ~ "VIAL + JERINGA",
    T ~ forma)) 

# check correction
pres_farma_master4 |> filter(nforma == raw_nformas[2]) |> 
  arrange(pres_farma_cod)
pres_farma_master4 |> filter(nforma == raw_nformas[3]) |> 
  arrange(pres_farma_cod)

```



```{r}
# fix nforma = raw_nformas[4, 5, 6, 7, 8]-------------------------------------
pres_farma_master4 |> filter(nforma %in% c(raw_nformas[4],
                                           raw_nformas[5],
                                           raw_nformas[6],
                                           raw_nformas[7],
                                           raw_nformas[8]
                                           )) |> 
  arrange(pres_farma_cod)

pres_farma_master5 <- pres_farma_master4 |> 
  mutate(nforma = case_when(
    pres_farma_cod == 6614 ~ "1",
    pres_farma_cod == 13684 ~ "28",
    pres_farma_cod == 14301 ~ "30",
    pres_farma_cod == 27403 ~ "1",
    pres_farma_cod == 27753 ~ "1",
    TRUE ~ nforma
  )) |> 
  mutate(forma = case_when(
    pres_farma_cod == 6614 ~ "SOL ORAL",
    pres_farma_cod == 13684 ~ "COMPRIMIDOS RECUBIERTOS",
    pres_farma_cod == 14301 ~ "GRAGEAS",
    pres_farma_cod == 27403 ~ "EMULSION",
    pres_farma_cod == 27753 ~ "SOLUCION",
    TRUE ~ forma
  ))

# check correction
pres_farma_master5 |> filter(nforma %in% c(raw_nformas[4],
                                           raw_nformas[5],
                                           raw_nformas[6],
                                           raw_nformas[7],
                                           raw_nformas[8]
                                           )) |> 
  arrange(pres_farma_cod)

```

```{r}
# fix nforma = raw_nformas[12]-------------------------------------------------
pres_farma_master5 |> filter(nforma %in% c(raw_nformas[12]
                                           )) |> 
  arrange(pres_farma_cod)

pres_farma_master6 <- pres_farma_master5 |> 
  mutate(nforma = case_when(
    pres_farma_cod == 28591 ~ "56",
    pres_farma_cod == 28592 ~ "56",
    TRUE ~ nforma
  )) |> 
  mutate(forma = case_when(
    pres_farma_cod == 28591 ~ "COMPRIMIDOS",
    pres_farma_cod == 28592 ~ "COMPRIMIDOS",
    TRUE ~ forma
  ))

# check correction
pres_farma_master6 |> filter(nforma %in% c(raw_nformas[12]
                                           )) |> 
  arrange(pres_farma_cod)

```

```{r}
# fix nforma = raw_nformas[16, 75]-------------------------------------------------
pres_farma_master6 |> filter(nforma %in% c(raw_nformas[16],
                                           raw_nformas[20],
                                           raw_nformas[25],
                                           raw_nformas[29],
                                           raw_nformas[38],
                                           raw_nformas[41],
                                           raw_nformas[57],
                                           raw_nformas[59],
                                           raw_nformas[62],
                                           raw_nformas[63],
                                           raw_nformas[64],
                                           raw_nformas[65],
                                           raw_nformas[66],
                                           raw_nformas[67],
                                           raw_nformas[68],
                                           raw_nformas[69],
                                           raw_nformas[70],
                                           raw_nformas[71],
                                           raw_nformas[72],
                                           raw_nformas[73],
                                           raw_nformas[74],
                                           raw_nformas[75]
                                           )) |> 
  arrange(pres_farma_cod)
                                           
                                           
pres_farma_master7 <- pres_farma_master6 |> 
  mutate(nforma = case_when(
    pres_farma_cod == 13967 ~ "1",
    pres_farma_cod == 25772 ~ "30",
    pres_farma_cod == 14194 ~ "30",
    pres_farma_cod == 25509 ~ "27",
    pres_farma_cod == 4027 ~ "1",
    pres_farma_cod == 27336 ~ "60",
    pres_farma_cod == 12841 ~ "1",
    pres_farma_cod == 24747 ~ "56",
    pres_farma_cod == 15094 ~ "40",
    pres_farma_cod == 27445 ~ "30",
    pres_farma_cod == 25579 ~ "1",
    pres_farma_cod == 26277 ~ "1",
    pres_farma_cod == 27584 ~ "1",
    pres_farma_cod == 28745 ~ "1",
    pres_farma_cod == 6712 ~ "1",
    pres_farma_cod == 6713 ~ "1",
    pres_farma_cod == 27600 ~ "30",
    nforma == "CAPSULAS" ~ NA_character_,
    nforma == "GEL" ~ "1",
    nforma == "POMADA" ~ "1",    
    nforma == "SOLUCION" ~ "1",
    nforma == "SUSP" ~ "1",
    nforma == "SUSPENSION" ~ "1",
    nforma == "SOLUCIÓN" ~ "1",
    nforma == "SOLUCIÓN" ~ "1",
    nforma == "SOBRES" ~ NA_character_,
    TRUE ~ nforma
  )) |> 
  mutate(forma = case_when(
    pres_farma_cod == 13967 ~ "JERINGA",
    pres_farma_cod == 25772 ~ "COMPRIMIDOS",
    pres_farma_cod == 14194 ~ "JERINGA",
    pres_farma_cod == 25509 ~ "COMPRIMIDOS",
    pres_farma_cod == 4027 ~ "VIAL",
    pres_farma_cod == 27336 ~ "COMPRIMIDOS",
    pres_farma_cod == 12841 ~ "SUSPENSION",
    pres_farma_cod == 24747 ~ "COMPRIMIDOS",
    pres_farma_cod == 15094 ~ "GRAGEAS",
    pres_farma_cod == 27445 ~ "COMPRIMIDOS",
    pres_farma_cod == 25579 ~ "CREMA",
    pres_farma_cod == 26277 ~ "SUSPENSION",
    pres_farma_cod == 27584 ~ "SUSPENSION",
    pres_farma_cod == 28745 ~ "SOLUCION",
    pres_farma_cod == 6712 ~ "SPRAY NASAL",
    pres_farma_cod == 6713 ~ "SPRAY NASAL",
    pres_farma_cod == 27600 ~ "COMPRIMIDOS",
    texto_forma == "CAPSULAS" ~ "CAPSULAS",
    texto_forma == "GEL" ~ "GEL",
    texto_forma == "POMADA" ~ "POMADA",
    texto_forma == "SOLUCION" ~ "SOLUCION",
    texto_forma == "SUSP" ~ "SUSPENSION ORAL",
    texto_forma == "SUSPENSION" ~ "SUSPENSION",
    texto_forma == "SOLUCIÓN" ~ "SOLUCIÓN",
    texto_forma == "SOBRES" ~ "SOBRES",
    TRUE ~ forma
  ))

# check correction
pres_farma_master7 |> filter(nforma %in% c(raw_nformas[16],
                                           raw_nformas[20],
                                           raw_nformas[25],
                                           raw_nformas[29],
                                           raw_nformas[38],
                                           raw_nformas[41],
                                           raw_nformas[57],
                                           raw_nformas[59],
                                           raw_nformas[62],
                                           raw_nformas[63],
                                           raw_nformas[64],
                                           raw_nformas[65],
                                           raw_nformas[66],
                                           raw_nformas[67],
                                           raw_nformas[68],
                                           raw_nformas[69],
                                           raw_nformas[70],
                                           raw_nformas[71],
                                           raw_nformas[72],
                                           raw_nformas[73],
                                           raw_nformas[74],
                                           raw_nformas[75]
                                           )) |> 
  arrange(pres_farma_cod)

```

## Fix formas

```{r}
# fix errors in nforma-------------------------------------------------------
raw_formas <- pres_farma_master7 |> distinct(forma) |> 
  arrange(forma) |> pull()

```


```{r}
# fix forma -----------------------------------------------------------------
pres_farma_master7 |> filter(forma %in% c(
  raw_formas[38],
  raw_formas[39],
  raw_formas[40],
  raw_formas[73]
                                          )) |> 
  arrange(pres_farma_cod)

pres_farma_master8 <- pres_farma_master7 |> 
  mutate(nforma = case_when(
    pres_farma_cod == 4841 ~  "1",
    pres_farma_cod == 14125 ~ "1",
    pres_farma_cod == 28691 ~ "1",
    pres_farma_cod == 17277 ~ "20", 
    pres_farma_cod == 10360 ~ "1", 
    pres_farma_cod == 22136 ~ "1", 
    T ~ nforma)) |>
  mutate(forma = case_when(
    pres_farma_cod == 4841 ~  "JERINGA",
    pres_farma_cod == 14125 ~ "JERINGA",
    pres_farma_cod == 28691 ~ "JERINGA",
    pres_farma_cod == 17277 ~ "GRAGEAS",
    pres_farma_cod == 10360 ~ "JERINGA",
    pres_farma_cod == 22136 ~ "JERINGA",
    T ~ forma)) 

# check correction
pres_farma_master8 |> filter(forma %in% c(
  raw_formas[38],
  raw_formas[39],
  raw_formas[40],
  raw_formas[73]
                                          )) |> 
  arrange(pres_farma_cod)

```

```{r}
# fix nforma as integer------------------------------------------------------
pres_farma_master9 <- pres_farma_master8 |> 
  mutate(nforma = as.integer(nforma)) |> 
  select(-texto_forma)  

```

```{r}
# add forma and nforma-------------------------------------------------------
gaia_clinical_drugs2 <- gaia_clinical_drugs |>
    left_join(pres_farma_master9, by = c("pres_farma_cod", "pres_farma_desc"))

```


# Add english names 

## Add act_desc

```{r}
# translate to english active principles-------------------------------------
gaia_act_desc <- gaia_clinical_drugs2 |> 
  distinct(prin_act_desc) |> arrange(prin_act_desc)

gaia_act_desc |> pull()

gaia_act_desc_english <- gaia_act_desc |> 
  mutate(prin_act_desc_english = c(
"abacavir",
"abacavir + lamivudine",
"abatacept",
"acarbose",
"aceclofenaco",
"acenocumarol",
"acetylcysteine",
"acetylsalicylic + chlorphenamine + phenylephrine",
"acetylsalicylic acid",
"acetylsalicylic acid + ascorbic acid",
"acetylsalicylic acid + caffeine",
"acetylsalicylic acid + codeine",
"acetylsalicylic acid + codeine + caffeine",
"acetylsalicylic acid + paracetamol + caffeine",
"aciclovir",
"cromoglicic acid",
"salicylic acid + fluorouracil",
"aclidinium",
"aclidinium + formoterol",
"adalimumab",
"adrenaline",
"agomelatine",
"seawater",
"albiglutide",
"aldesleukin",
"alemtuzumab",
"aliskiren",
"aliskiren + hydrochlorothiazide",
"almotriptan",
"alogliptin",
"alogliptin + metformin",
"alogliptin + pioglitazone",
"alprazolam",
"alteplase",
"altizide + spironolactone",
"amantadine",
"ambisentan",
"ambroxol",
"amphotericin b",
"amikacin",
"amiloride hydrochloride",
"aminolevulinic acid",
"amiodarone",
"amiodarone hydrochloride",
"amisulpride",
"amitriptyline",
"amitriptyline + medazepam",
"amlodipine",
"amlodipine + ramipril",
"amoxicillin",
"amoxicillin + clavulanic acid",
"ampicillin",
"ampicillin + ampicillin benzatine",
"anagrelide",
"anakinra",
"anastrozole",
"hepatitis a antigen",
"hepatitis b antigen + hepatitis a antigen",
"meningococcal polysaccharide antigen a,c,w,y",
"hepatitis b surface antigen",
"influenza virus surface antigen",
"salmonella typhi capsular polysaccharide vi antigen",
"apixaban",
"apremilast",
"aripiprazole",
"artemisinin + piperaquine tetrafosfate tetrahydrate",
"asenapine",
"atazanavir",
"atenolol",
"atenolol + bendroflumethiazide",
"atenolol + chlorthalidone",
"atenolol + hydrochlorothiazide + amiloride",
"atomoxetine",
"atovaquine",
"atovacuona + proguanil",
"azathioprine",
"azelastine",
"azelastine + fluticasone",
"azithromycin",
"aztreonam",
"b.pertussis + t. tetanico + t. difterico",
"bambuterol",
"baricitinib",
"barnidipine",
"bcg atenuado",
"beclometasone",
"beclometasone + formoterol + glycopyrronium",
"beclometasone dipropionate + formoterol fumarate dihydrate",
"belimumab",
"bemiparin",
"benazepril",
"benazepril + hydrochlorothiazide",
"benzylpenicillin",
"benzylpenicillin (sodium - procaine - benzathine)",
"benzylpenicillin (sodium + benzathine) + phenoxymethylpenicillin",
"benralizumab",
"bentazepam",
"benznidazole",
"betamethasone",
"bevacizumab",
"bexarotene",
"bicalutamide",
"bisoprolol",
"bisoprolol + hydrochlorothiazide",
"bordetella pertussis toxoid + bordetella pertussis filamentous hemagglutinin + bordetella pertussis pertactin + polio virus type I + polio virus type II + polio virus type III + diphtheria toxoid + tetanus toxoid",
"bosentan",
"brivudine",
"brodalumab",
"bromazepam",
"bromhexine",
"bromhexine + diphenhydramine + codeine + ephedrine",
"tiotropium bromide (DPI)",
"brotizolam",
"budesonide",
"bumetanide",
"buprenorphine",
"bupropion",
"caffeine",
"canagliflozin",
"canagliflozin + metformin",
"canakinumab",
"candesartan",
"candesartan + hydrochlorothiazide",
"capecitabine",
"captopril",
"captopril + hydrochlorothiazide",
"carbocisteine",
"carbocisteine + promethazine",
"cariprazine",
"carvedilol",
"carvedilol + ivabradine",
"cefaclor",
"cefadroxil",
"cefalexin",
"cefalexin monohydrate",
"cefazolin",
"cefditoren",
"cefepime",
"cefixime",
"cefotaxime",
"cefoxitin",
"ceftazidime",
"ceftazidime + avibactam",
"ceftriaxone",
"cefuroxime",
"celecoxib",
"celiprolol",
"certolizumab pegol",
"cetirizine + pseudoephedrine",
"ciclesonide",
"cyclophosphamide",
"cyclosporine",
"cilazapril",
"cilazapril + hydrochlorothiazide",
"cilostazol",
"cimetidine",
"ciprofloxacin",
"citalopram",
"citicholine",
"cladribine",
"clarithromycin",
"clindamycin",
"clindamycin hydrochloride",
"clindamycin HCl + triamcinolone acetonide",
"clobazam",
"clomethiazole",
"clomipramine",
"clonidine",
"clonidine hydrochloride",
"clonixinate lysine",
"cloperastine",
"clopidogrel",
"clopidogrel + acetylsalicylic acid",
"chlorambucil",
"clorazepate dipotassium",
"chlorcyclizine + guaifenesin + codeine + cineole",
"chlorodiazepoxide",
"chlorphenamine + codeine + pseudoephedrine",
"chlorphenamine + dexamethasone + neomycin + lysozyme",
"chlorphenamine + dextromethorphan + ephedrine",
"chlorphenamine + diphenhydramine + phenylephrine",
"chlorphenamine + paracetamol + pseudoephedrine",
"chloroquine",
"chlorpromazine",
"chlorthalidone",
"chlorthalidone + spironolactone",
"clozapine",
"clotiazepam",
"cloxacillin",
"clozapine",
"cobisitat + atazanavir",
"cobisitat + tenofovir (TAF) + emtricitabine + darunavir",
"codeine",
"colistimethate",
"colistin",
"pregnancy and lactation dietary supplement",
"chondroitin sulfate",
"cotrimoxazole (sulfamethoxazole + trimethoprim)",
"dabigatran",
"daclatasvir",
"dalteparin",
"dapagliflozin",
"dapsone",
"dapsone + iron oxalate",
"darunavir",
"darunavir + cobicistat",
"dasabuvir",
"deanol + heptaminol",
"deflazacort",
"delapril + manidipine",
"desvenlafaxine",
"dexamethasone",
"dexibuprofen",
"dexketoprofen",
"dexketoprofen + tramadol",
"dextromethorphan",
"dextromethorphan + sodium benzoate",
"dextromethorphan + benzocaine + benzoate + guaiacol",
"dextromethorphan + chlorphenamine + paracetamol",
"dextromethorphan + phenylpropanolamine",
"dextromethorphan + diphenhydramine",
"dextromethorphan + phenylephrine",
"dextromethorphan + guaifenesin",
"dextromethorphan + pseudoephedrine",
"dextromethorphan + pseudoephedrine + triprolidine",
"diacerin",
"diazepam",
"diazepam + pyridoxine",
"diclofenac",
"diclofenac + misoprostol",
"didanosine",
"diphtheria + pertussis + tetanus + h. influenzae + polio",
"dihydrocodeine",
"dihydroergocristine",
"dihydroergocristine + cinnarizine",
"dihydroergocristine + piracetam",
"diltiazem",
"diltiazem hydrochloride",
"dipyridamole",
"disopyramide",
"dolutegravir",
"dolutegravir + abacavir + lamivudine",
"dolutegravir + lamivudine",
"dolutegravir + rilpivirine",
"donepezil",
"doravirine",
"doxazosin",
"doxepin",
"doxycycline",
"doxorubicin",
"dronabinol + cannabidiol",
"dronedarone",
"drosera fluid extract + thyme fluid extract",
"dulaglutide",
"duloxetine",
"ebastine + pseudoephedrine",
"eculizumab",
"edoxaban",
"efavirenz",
"efavirenz + tenofovir + emtricitabine",
"ephedrine",
"eletriptan",
"elvitegravir + cobicistat + emtricitabine + tenofovir",
"empagliflozin",
"empagliflozin + linagliptin",
"emtricitabine + rilpivirine + tenofovir alafenamide",
"emtricitabine + rilpivirine + tenofovir disoproxil fumarate",
"enalapril",
"enalapril + hydrochlorothiazide",
"enalapril + nitrendipine",
"enoxaparin",
"entecavir",
"eplerenone",
"epoetin alfa",
"epoetin beta",
"epoetin zeta",
"epoprostenol",
"eprosartan",
"eprosartan + hydrochlorothiazide",
"erenumab",
"ergotamine + caffeine",
"ergotamine + paracetamol + caffeine",
"erythromycin",
"ertapenem",
"ertugliflozin",
"ertugliflozin + metformin",
"escitalopram",
"spiramycin",
"spiramycin + metronidazole",
"spironolactone",
"streptomycin",
"streptokinase + streptodornase",
"ethambutol",
"ethambutol + isoniazid + pyrazinamide + rifampicin",
"etanercept",
"ethylfrine",
"etoposide",
"etoricoxib",
"etravirine",
"everolimus",
"exemestane",
"exenatide",
"famciclovir",
"famotidine",
"felodipine",
"felodipine + ramipril",
"phenazopyridine + sulfamethizole",
"phenylephrine",
"phenytoin",
"phenoxymethylpenicillin",
"fentanyl",
"filgotinib",
"filgrastim",
"fingolimod",
"flecainide",
"fluconazole",
"fludarabine",
"fludrocortisone",
"fludrocortisone acetate",
"fluphenazine",
"fluoxetine",
"flupentixol",
"flurazepam",
"flutamide",
"fluticasone",
"fluvoxamine",
"fondaparinux",
"formoterol",
"formoterol + budesonide",
"formoterol + fluticasone",
"fosamprenavir",
"phosphoglycoprotein",
"fosfomycin",
"fosinopril",
"fosinopril + hydrochlorothiazide",
"fremanezumab",
"frovatriptan",
"fulvestrant",
"furosemide",
"furosemide + triamterene",
"fusidic acid",
"g-aminobutyric acid + magnesium glutamate + pyridoxine",
"galantamine",
"galcanezumab",
"anti-Rh immunoglobulin",
"anti-hepatitis B immunoglobulin",
"anti-rabies immunoglobulin",
"anti-tetanus immunoglobulin",
"gentamicin",
"ginkgo biloba",
"glatiramer acetate",
"glecaprevir + pibrentasvir",
"glibenclamide",
"gliclazide",
"glycopyrronium",
"glimepiride",
"glipizide",
"glisentide",
"glucosamine",
"glutamic acid",
"golimumab",
"guar gum",
"goserelin",
"grazoprevir + elbasvir",
"guaifenesin",
"guaifenesin + diprophylline + betamethasone",
"guaifenesin + pseudoephedrine",
"guaifenesin + pseudoephedrine + triprolidine",
"guanfacine",
"guselkumab",
"haloperidol",
"hederahelix leaf hydroalcoholic extract",
"heparin",
"hyaluronic acid",
"hydralazine",
"hydrochlorothiazide",
"hydrochlorothiazide + amiloride",
"hydrocortisone",
"hydromorphone",
"hydroquinidine",
"hydroxycarbamide",
"hydroxychloroquine",
"hydroxyzine",
"hydroxyzine hydrochloride + cimetidine",
"ibuprofen",
"ibuprofen + codeine",
"ibuprofen + pseudoephedrine",
"idebenone",
"iloprost",
"imidapril",
"imipramine",
"indacaterol",
"indacaterol + glycopyrronium",
"indacaterol + mometasone",
"indapamide",
"indomethacin",
"indomethacin + metronidazole + ivermectin",
"indomethacin + prednisone",
"infliximab",
"human immunoglobulin G",
"human normal immunoglobulin",
"insulin aspart",
"insulin aspart + insulin aspart protamine",
"intermediate-acting insulin aspart",
"biphasic insulin",
"insulin degludec",
"insulin detemir",
"insulin glargine",
"insulin glulisine",
"intermediate-acting human insulin",
"rapid-acting human insulin",
"isophane insulin",
"rapid-acting insulin lispro",
"intermediate-acting insulin lispro 50:50",
"intermediate-acting insulin lispro 25:75",
"interferon alpha",
"interferon alpha-2b",
"human interferon beta",
"ipratropium",
"ipratropium + salbutamol",
"irbesartan",
"irbesartan + hydrochlorothiazide",
"irbesartan + hydrochlorothiazide (300/25) mg",
"irbesartan + hydrochlorothiazide (150/12.5) mg",
"isavuconazole",
"isoniazid",
"isoniazid + pyridoxine",
"isonixine",
"isosorbide",
"isosorbide dinitrate",
"isosorbide mononitrate",
"itraconazole",
"ivabradine",
"ixekizumab",
"josamycin",
"ketazolam",
"ketoprofen",
"ketorolac",
"labetalol",
"lacidipine",
"lamivudine",
"ledipasvir + sofosbuvir",
"leflunomide",
"lenalidomide",
"lenograstim",
"lercanidipine",
"lercanidipine + enalapril",
"letrozole",
"leuprorelin",
"levocabastine",
"levodropropizina",
"levofloxacin",
"levomepromazine",
"linagliptina",
"linagliptina + metformina",
"lincomicina",
"linezolid",
"lipoproteina recombinante fhbp de neisseria meningitidis del serogrupo b subfamilia a + subfamilia b",
"liraglutida",
"lisdexanfetamina",
"lisinopril",
"lisinopril + hidroclorotiazida",
"litio",
"lixisenatida",
"lomustina",
"loprazolam",
"loratadina + pseudoefedrina",
"lorazepam",
"lormetazepam",
"lornoxicam",
"losartan",
"losartan + hidroclorotiazida 50/12,5",
"losartan + hidroclorotiazida 100/12,5",
"losartan + hidroclorotiazida 100/25",
"loxapina",
"lurasidona",
"macitentan",
"manidipino",
"maprotilina",
"maraviroc",
"medroxiprogesterona",
"mefenamic acid",
"megestrol",
"meglumine",
"melatonin",
"melitracen + flupentixol",
"meloxicam",
"memantina",
"meningococcal b vaccine",
"mepiramine",
"mepolizumab",
"mercaptopurine",
"meropenem",
"mesna",
"metamizole",
"metformin",
"metformin + dapagliflozin",
"metformin + empagliflozin",
"metformin + pioglitazone",
"metformin + sitagliptin",
"metformin + vildagliptin",
"methyldopa",
"methylphenidate",
"methylprednisolone",
"metoprolol",
"metoprolol + felodipine",
"methotrexate",
"metronidazole",
"mexiletine",
"mirtazapine",
"mycophenolic acid",
"midazolam",
"midecamycin",
"midodrine",
"minocycline",
"minoxidil",
"mirtazapine",
"mitomycin",
"mitotane",
"moclobemide",
"modafinil",
"molsidomine",
"mometasone",
"montelukast",
"morphine",
"morphine hydrochloride",
"moxifloxacin",
"moxonidine",
"nabumetone",
"nadolol",
"nadroparin",
"naphazoline",
"naftidrofuryl",
"naproxen",
"naproxen + esomeprazole",
"naratriptan",
"natalizumab",
"nebivolol",
"nebivolol + hydrochlorothiazide",
"nedocromil",
"nevirapine",
"nicardipine",
"nicergoline",
"methyl nicotinate",
"nifedipine",
"niflumic acid",
"nifurtimox",
"nimodipine",
"niraparib",
"nisoldipine",
"nitrendipine",
"nitrofurantoin",
"nitroglycerin",
"nitroglycerin + caffeine",
"norfloxacin",
"nortriptyline",
"nortriptyline + diazepam",
"noscapine",
"ocrelizumab",
"ofloxacin",
"olanzapine",
"olaparib",
"olmesartan",
"olmesartan + amlodipine",
"olmesartan + amlodipine + hydrochlorothiazide",
"olmesartan + hydrochlorothiazide",
"olodaterol",
"olodaterol + tiotropium bromide",
"omalizumab",
"ombitasvir + paritaprevir + ritonavir",
"orlistat",
"oseltamivir",
"oxycodone",
"oxycodone + naloxone",
"oxymetazoline",
"oxymetazoline + menthol",
"paliperidone",
"paracetamol",
"paracetamol + acetylcysteine",
"paracetamol + ascorbic acid",
"paracetamol + caffeine",
"paracetamol + caffeine + brompheniramine",
"paracetamol + caffeine + dimenhydrinate",
"paracetamol + chlorphenamine + dextromethorphan + ascorbic acid + caffeine",
"paracetamol + codeine",
"paracetamol + codeine + ascorbic acid",
"paracetamol + codeine + caffeine",
"paracetamol + phenylephrine + chlorphenamine",
"paracetamol + propyphenazone + caffeine",
"paracetamol + tramadol",
"paroxetine",
"pegfilgrastim",
"peginterferon alfa-2a",
"peginterferon beta-1a",
"penicillamine",
"pentoxifylline",
"perphenazine",
"perphenazine + amitriptyline",
"periciazine",
"perindopril",
"perindopril + amlodipine",
"perindopril + amlodipine + indapamide",
"perindopril + indapamide",
"pethidine",
"pimozide",
"pinazepam",
"pioglitazone (d.c.i.-r)",
"pioglitazone + glimepiride",
"pipemidic acid",
"piracetam",
"pyrazinamide",
"pirfenidone",
"pyrimethamine",
"pirisudanol",
"piroxicam",
"pneumococcal capsular polysaccharides",
"pneumococcal capsular polysaccharides serotypes 4,6B,9V,14,19F,23F + oligosaccharide 18C",
"pneumococcal polysaccharides serotypes 1,2,3,4,5,6B,7F,8,9N,9V,10A,11A,12F,14,15B,17F,18C,19A,19F,20,22F,23F,33F",
"pomalidomide",
"posaconazole",
"prasugrel",
"prazosin",
"prednisolone",
"prednisone",
"corticosteroid nasal preparations",
"propafenone",
"propranolol",
"human plasma protein",
"plasma proteins",
"pseudoephedrine",
"pseudoephedrine + dexbrompheniramine",
"quazepam",
"quetiapine",
"quinapril",
"quinapril + hydrochlorothiazide",
"raltegravir",
"ramipril",
"ramipril + hydrochlorothiazide",
"ranitidine",
"ranolazine",
"reboxetine",
"repaglinide",
"reslizumab",
"retinol",
"rh dnase",
"ribavirin",
"rifabutin",
"rifampicin",
"rifampicin + isoniazid",
"rifampicin + isoniazid + pyrazinamide",
"rilpivirine",
"riociguat",
"risankizumab",
"risperidone",
"ritonavir",
"ritonavir + lopinavir",
"rivaroxaban",
"rivastigmine",
"rizatriptan",
"roflumilast",
"rotavirus",
"roxithromycin",
"sacubitril + valsartan",
"salbutamol",
"salbutamol + beclometasone",
"salmeterol",
"salmeterol + fluticasone (25/50)",
"salmeterol + fluticasone (12,75/100)",
"salmeterol + fluticasone (12,75/202)",
"salmeterol + fluticasone (25/125)",
"salmeterol + fluticasone (25/250)",
"salmeterol + fluticasone (50/100)",
"salmeterol + fluticasone (50/250)",
"salmeterol + fluticasone (50/500)",
"salmonella typhi inactivated + salmonella typhi live",
"sarilumab",
"saxagliptin",
"saxagliptin + metformin",
"secukinumab",
"selexipag",
"semaglutide",
"sertindole",
"sertraline",
"siponimod",
"sirolimus",
"sitagliptin",
"sobrerol",
"sodium chloride",
"sofosbuvir",
"sotalol",
"sulfadiazine",
"sulfamethizole + phenazopyridine",
"sulfamethoxazole + sulfoguaiacol + trimethoprim",
"sulodexide",
"sulpiride",
"sulpiride + diazepam",
"sulpiride + diazepam + pyridoxine",
"sumatriptan",
"tacrolimus",
"thalidomide",
"tamoxifen",
"tapentadol",
"tegafur",
"telbivudine",
"telithromycin",
"telmisartan",
"telmisartan + amlodipine",
"telmisartan + hydrochlorothiazide",
"temozolomide",
"tenofovir",
"tenofovir (TAF) + bictegravir + emtricitabine",
"tenofovir + emtricitabine",
"tenoxicam",
"theophylline",
"terbutaline",
"terbutaline + guaifenesin",
"teriflunomide",
"tianeptine",
"tiapride",
"ticagrelor",
"ticlopidine",
"tildrakizumab",
"tinidazole",
"tinzaparin",
"tobramycin",
"tocilizumab",
"tofacitinib",
"tolvaptan",
"torasemide",
"diphtheria toxoid + tetanus toxoid",
"tetanus toxoid + meningococcal polysaccharide antigen group C",
"tramadol",
"tramazoline",
"trandolapril",
"trandolapril + verapamil",
"trazodone",
"treprostinil",
"tretinoin",
"triamcinolone",
"triamcinolone acetonide",
"triazolam",
"trifluridine + tipiracil",
"triflusal",
"trimetazidine",
"trimethoprim",
"trimethoprim + sulfamethoxazole + bromhexine + tolu balsam",
"trimipramine",
"triptorelin",
"ubidecarenone",
"umeclidinium",
"upadacitinib",
"urea",
"urokinase",
"ustekinumab",
"valacyclovir",
"valerian",
"valganciclovir",
"valsartan",
"valsartan + amlodipine",
"valsartan + amlodipine + hydrochlorothiazide",
"valsartan + hydrochlorothiazide",
"vancomycin",
"vedolizumab",
"velpatasvir + sofosbuvir",
"venetoclax",
"venlafaxine",
"verapamil",
"vibrio cholerae + recombinant cholera toxin",
"vilanterol + fluticasone",
"vilanterol + umeclidinium",
"vilanterol + umeclidinium + fluticasone",
"vildagliptin",
"vincamine + piracetam",
"vinorelbine",
"vinpocetine",
"inactivated Japanese encephalitis virus strain SA 14-2",
"yellow fever virus strain 17D",
"inactivated enteric influenza virus",
"split influenza virus",
"recombinant adjuvanted human papillomavirus (types 16 and 18)",
"human papillomavirus (types 6, 11, 16, 18)",
"human papillomavirus (types 6, 45, 18, 52, 16, 11, 58, 31, 33)",
"human papillomavirus type 16 L1 protein",
"rabies virus",
"measles + mumps + rubella virus",
"live attenuated varicella-zoster virus",
"vismodegib",
"voriconazole",
"vortioxetine",
"voxilaprevir + sofosbuvir + velpatasvir",
"warfarin",
"xylometazoline + ipratropium",
"xipamide",
"dry ivy extract",
"zafirlukast",
"zanamivir",
"zidovudine",
"zidovudine + lamivudine",
"ziprasidone",
"zolmitriptan",
"zolpidem",
"zopiclone",
"zuclopenthixol"
  ))

```

```{r}
# check names----------------------------------------------------------------
gaia_act_desc_english |> gt()
# ok

```

## Add form_name

```{r}
# translate to english forms-------------------------------------------------
gaia_forms <- gaia_clinical_drugs2 |> 
  distinct(forma) |> arrange(forma) 

gaia_forms |> pull(forma)

gaia_forms_english <- gaia_forms |> 
  mutate(form = c(
    # "AEROSOL"
    "aerosol",
    # "AMPOLLA"
    "ampoule",
    # "AMPOLLAS"
    "ampoule",
    # "BOLSAS"
    "bags",
    # "CAPSULAS"
    "capsule",
    # "CAPSULAS LIBERACION RETARDADA"
    "capsule",
    # "CARAMELOS"
    "candies",
    # "CARTUCHO"
    "cartridge",
    # "CARTUCHO/PLUMA"
    "cartridge/pen",
    # "COMPRIMIDO"
    "tablet",
    # "COMPRIMIDOS"
    "tablet",
    # "COMPRIMIDOS RECUBIERTOS"
    "tablet",
    # "COMPRIMIDOS SUBLINGUALES"
    "sublingual tablet",
    # "COMPRIMIDOS/TABLETAS"
    "tablet",
    # "CONCENTRADO"
    "concentrate",
    # "CREMA"
    "cream",
    # "DOSIS"
    "dose",
    # "EMULSION"
    "emulsion",
    # "ENEMA"
    "enema",
    # "EXTRACTO"
    "extract",
    # "FRASCO"
    "bottle",
    # "FRASCOS"
    "bottle",
    # "FRASCOS/BOLSAS"
    "bottle",
    # "GEL"
    "gel",
    # "GOTAS"
    "drops",
    # "GOTAS NASALES"
    "nasal drops",
    # "GRAGEAS"
    "coated tablets",
    # "GRANULADO PARA SUSPENSION ORAL"
    "granules for oral suspension",
    # "INHALACIONES"
    "inhalation",
    # "INHALACIÓN"
    "inhalation",
    # "INHALADOR"
    "inhaler",
    # "INYECTABLE"
    "injectable",
    # "INYECTABLES"
    "injectable",
    # "JARABE"
    "syrup",
    # "JERINGA"
    "syringe",
    # "JERINGA/PLUMA"
    "syringe",
    # "LIOTABS"
    "liotab",
    # "MONODOSIS"
    "unit dose",
    # "NEBULIZACION"
    "nebulization",
    # "NEBULIZACION/INHALACION"
    "nebulization",
    # "NEBULIZADOR"
    "nebulizer",
    # "ORAL"
    "oral suspension",
    # "PARA"
    "solution",
    # "PARCHE"
    "patch",
    # "PARCHE TRANSDERMICO"
    "transdermal patch",
    # "PARCHES"
    "patch",
    # "PASTILLAS"
    "pills",
    # "PELICULAS"
    "films",
    # "PLUMA"
    "pen",
    # "PLUMA PREGARGADA"
    "pre-filled pen",
    # "PLUMAS"
    "pen",
    # "POLVO"
    "powder",
    # "POMADA"
    "ointment",
    # "PULSACIONES"
    "pulses",
    # "PULVERIZACIONES"
    "sprays",
    # "PULVERIZADOR"
    "sprayer",
    # "SOBRE"
    "sachet",
    # "SOBRES"
    "sachet",
    # "SOL"
    "solution",
    # "SOL ORAL"
    "solution",
    # "SOLUCION"
    "solution",
    # "SOLUCION GOTAS"
    "solution",
    # "SOLUCION PARA PULVERIZACION NASAL"
    "solution",
    # "SPRAY"
    "spray",
    # "SPRAY NASAL"
    "spray",
    # "SUPOSITORIOS"
    "suppositories",
    # "SUSP"
    "suspension",
    # "SUSPENSION"
    "suspension",
    # "TABLETAS"
    "tablets",
    # "VIAL"
    "vial",
    # "VIAL + JERINGA"
    "vial + syringe"
))

```

```{r}
# add english descriptions---------------------------------------------------
gaia_clinical_drugs3 <- gaia_clinical_drugs2 |> 
  left_join(gaia_act_desc_english) |> 
  left_join(gaia_forms_english)

```

# Fix via_desc

In the variable *via_desc*, there is one category called "OTRAS VIAS". We will specify what route they are referring to. Particularly, there are two drug forms: a transdermal patch and a subcutaneous injection. 

```{r}
# update via_desc recoding "OTRAS VIAS" Category-----------------------------
gaia_clinical_drugs3 |> distinct(via_desc) |> arrange(via_desc)
gaia_clinical_drugs3 |> filter(via_desc == "OTRAS VIAS")
gaia_clinical_drugs3 |> filter(pres_farma_cod %in% c(10281, 10812))
gaia_clinical_drugs4 <- gaia_clinical_drugs3 |> mutate(
  via_desc = case_when(
    pres_farma_cod == "10281" ~ "TRANSDERMAL",
    pres_farma_cod == "10812" ~ "SUBCUTANEA",
    T ~ via_desc))
    
```

# Group pres_farma_cod

The *pres_farma_cod* should be unique, so we merge two categories that have two different, albeit similar, descriptions.

```{r}
# group repeated pres_farma_cod----------------------------------------------
gaia_clinical_drugs4 |> add_count(pres_farma_cod) |> 
  filter(n > 1)

gaia_clinical_drugs5 <- gaia_clinical_drugs4 |> 
  group_by(pres_farma_cod) |> 
  summarise_all(dplyr::first)

```

# Save gaia

```{r}
# save master----------------------------------------------------------------
fwrite(gaia_clinical_drugs5, file.path("Resultados", "gaia_masters",
                                      "gaia_clinical_drugs5.csv"))

```

# Create file to use with usagi

```{r}
# create and save usagi_gaia-------------------------------------------------
usagi_gaia <- gaia_clinical_drugs5 |> 
  count(pres_farma_cod, pres_farma_desc)

usagi_gaia_sin_barra <- gaia_clinical_drugs5 |> 
  count(pres_farma_cod, pres_farma_desc) |> 
  mutate(pres_farma_desc = str_remove_all(pres_farma_desc, "/"))


fwrite(usagi_gaia, file.path("Resultados", "gaia_masters", "usagi",
                                      "usagi_gaia.csv"))
fwrite(usagi_gaia_sin_barra, file.path("Resultados", "gaia_masters", "usagi",
                                      "usagi_gaia_sin_barra.csv"))

```





```{r}
#| include: false
# copy .qmd to CERES---------------------------------------------------------
unlink(file.path("F:", "CERES2", "CONSIGN_SD2270", "2-SCRIPTS", "R",
                 "1_07_5_GAIA_Standard_Concepts_CONSIGN.qmd"))
file.copy(from = file.path("1_07_5_GAIA_Standard_Concepts_CONSIGN.qmd"),
          to = file.path("F:", "CERES2", "CONSIGN_SD2270",
                         "2-SCRIPTS", "R"))

```

<div class="tocify-extend-page" data-unique="tocify-extend-page" style="height: 0;"></div>
