---
title: "OMOP ETL Implementation: CONSIGN"
author: "Francisco Sanchez-Saez"
date: "last-modified"
editor: source
format:
  html:
    toc: true
    toc-location: left
    theme: cerulean
    highlight-style: breeze
    css: style.css
    embed-resources: true
---

```{r}
#| echo: false
source("_common.R")
knitr::opts_chunk$set(
  eval = FALSE
)

```

```{r }
#| eval: true
#| include: false
# load libraries and functions-----------------------------------------------
source(file.path("..", "scripts", "Librerias.R"))
source(file.path("..", "scripts", "Funciones.R"))

```

```{css, echo = FALSE}
.output {
max-height: 500px;
overflow-y: scroll;
}

```

# Load source tables: part one

The following origin tables contain data from the CONSIGN project. In the first part, we load **SIP** and **MBDS** origin tables.

```{r}
# select origin_tables or samples--------------------------------------------
origin_tables <- file.path("..", "consign", "Origin_tables")

```

```{r}
# load tables----------------------------------------------------------------
# first part
sip       <- fread(file.path(origin_tables, "sip.csv"), encoding = "UTF-8")
mbds      <- fread(file.path(origin_tables, "mbds.csv"), encoding = "UTF-8")
# pmr       <- fread(file.path(origin_tables, "pmr.csv"), encoding = "UTF-8")
sips_consign <- readRDS(file.path("..", "consign", "Resultados", "sips",
                                  "sips_consign.RDS"))

```

Initiate the data transformation process by creating the **care_site** target table. This step is necessary as we need to define the **care_site_id**, which will be used in the **person** table.

# care_site

## From sip to care_site

```{r}
# populate table-------------------------------------------------------------
from_sip_to_care_site <- sip |>
  distinct(dpto_salud, zona_salud) |> 
  separate_wider_delim(dpto_salud, delim = ":", 
                       names = c("dpto_salud_cod", "dpto_salud_desc"),
                       too_few = "align_start", cols_remove = FALSE) |> 
  separate_wider_delim(zona_salud, delim = ":",
                       names = c("zona_salud_cod", "zona_salud_desc"),
                       too_few = "align_start", cols_remove = FALSE) |>
  mutate(across(c(dpto_salud_cod, zona_salud_cod), as.integer)) |> 
  arrange(dpto_salud_cod, zona_salud_cod) |> 
  transmute(
         care_site_id = 1:n(),
         care_site_name = glue("{dpto_salud_desc}; {zona_salud_desc}"),
         place_of_service_concept_id = 38004226,
         location_id = NA_integer_,
         care_site_source_value = glue("{dpto_salud_cod}; {zona_salud_cod}"),
         place_of_service_source_value = "Zona básica de salud",
         dpto_salud,
         zona_salud
         )

last_sip_care_site_id <- max(from_sip_to_care_site$care_site_id)

```


```{r}
# write table----------------------------------------------------------------
fwrite(from_sip_to_care_site, file = file.path("Target_tables",
       "AUXILIAR", "from_sip_to_care_site.csv"))

from_sip_to_care_site_write <- from_sip_to_care_site |> 
  select(-dpto_salud, -zona_salud)

fwrite(from_sip_to_care_site_write, append = FALSE,
       file = file.path("Target_tables",
                        "care_site_vid.csv"))

```

## From mbds (hospitals) to care_site

```{r}
# load master of hospital_cod to obtain hospital names-----------------------
master_hospitals <- read_excel(file.path("z:", "0-RECURSOS", "4-MAESTROS", 
                     "Hospitales_codigo.xlsx")) |> 
  clean_names() |> 
  transmute(hosp_cod = cent_cod |> as.integer(),
            hosp_desc = centdesc_lar) |> 
  arrange(hosp_cod)

```


```{r}
# populate table-------------------------------------------------------------
from_mbds_to_care_site <- master_hospitals |> 
  transmute(
         care_site_id = 1:n() + last_sip_care_site_id,
         care_site_name = str_remove_all(hosp_desc, ","),
         place_of_service_concept_id = 38004515,
         location_id = NA_integer_,
         care_site_source_value = hosp_cod,
         place_of_service_source_value = "Hospital"
         )

# write table----------------------------------------------------------------
fwrite(from_mbds_to_care_site, append = TRUE,
       file = file.path("Target_tables",
                        "care_site_vid.csv"))

```

<br>

Next, we proceed with the creation of the **person** target table. This table will store the information related to individuals in our dataset.

# person

## From sip to person

```{r}
# populate table-------------------------------------------------------------
from_sip_to_person <- sip |>
  select(sip,
         fecha_nacimiento,
         fecha_defuncion,
         pais_nacimiento,
         sexo,
         fecha_calculo,
         dpto_salud,
         zona_salud) |>
  # fill care_site_id
  mutate(care_site_source_value = glue("{dpto_salud}; {zona_salud}")) |>
  left_join(from_sip_to_care_site |> 
              select(care_site_id, dpto_salud, zona_salud),
            by = c("dpto_salud", "zona_salud")) |> 
  # select 'fecha_nacimiento', 'fecha_defuncion', and 'pais_nacimiento' updated)
  group_by(sip) |> 
  slice(which.max(fecha_calculo)) |> 
  ungroup() |> 
  transmute(person_id = 1:n(),
            gender_concept_id = case_when(sexo == 'Male' ~ 8507, 
                                          sexo == 'Female' ~ 8532, 
                                          T ~ NA_integer_),
            year_of_birth	 = str_sub(fecha_nacimiento, 1, 4) |> as.integer(),
            month_of_birth = str_sub(fecha_nacimiento, 6, 7) |> as.integer(),
            day_of_birth   = str_sub(fecha_nacimiento, 9, 10) |> as.integer(),
            birth_datetime = fecha_nacimiento,
            race_concept_id = 0,
            ethnicity_concept_id = 0,
            location_id = NA_integer_,
            provider_id = NA_integer_,
            care_site_id = care_site_id,
            person_source_value = sip,
            gender_source_value = sexo,
            gender_source_concept_id = 0,
            race_source_value = NA_character_,
            race_source_concept_id = 0,
            ethnicity_source_value = NA_character_,
            ethnicity_source_concept_id = 0,
            fecha_defuncion
            )

# write table----------------------------------------------------------------
fwrite(from_sip_to_person, append = FALSE,
       file = file.path("Target_tables", "AUXILIAR",
                        "from_sip_to_person.csv"))

# save person_id <-> sip relationship
person_ids <- from_sip_to_person |> select(person_id, person_source_value) 

fwrite(person_ids, append = FALSE,
       file = file.path("Target_tables", "AUXILIAR",
                        "person_ids.csv"))

person_ids <- fread(file = file.path("Target_tables", "AUXILIAR",
                        "person_ids.csv"))


from_sip_to_person_write <- from_sip_to_person |> select(-fecha_defuncion)

# write table----------------------------------------------------------------
fwrite(from_sip_to_person_write, append = FALSE,
       file = file.path("Target_tables",
                        "person_vid.csv"))


```

# observation_period

## From sip to observation_period

```{r}
# # union of consecutive years with observation------------------------------
# sip_periods_0 <- sip |>
#   select(sip, fecha_calculo) |>
#   mutate(inicio = ymd(glue("{year(fecha_calculo)}0101")),
#          final = fecha_calculo %m+% days(1)) |>
#   group_by(sip) |>
#   mutate(periodo = c(1, 1 + cumsum(as.numeric(lead(inicio)) >
#                               cummax(as.numeric(final)))[-n()])) |>
#   group_by(sip, periodo) |>
#   summarise(min_inicio = min(inicio),
#             max_final = max(final) %m-% days(1)) |>
#   ungroup() |>
# # transform sip_grouped----------------------------------------------------
# rename(fecha_inicio = min_inicio,
#        fecha_fin = max_final) |>
# # add fecha_defuncion
# left_join((sip |> distinct(sip, fecha_defuncion))) |>
#   tidylog::distinct() |>
#   mutate(fecha_fin = pmin(fecha_fin, fecha_defuncion, na.rm = TRUE))
# 
# # check distinct periods and death date------------------------------------
# sip_periods_0 |> count(periodo)
# sip_periods_0 |> filter(!is.na(fecha_defuncion))
# 
# # write table--------------------------------------------------------------
# fwrite(sip_periods_0, append = FALSE,
#        file = file.path("Target_tables", "AUXILIAR",
#                         "sip_periods_0.csv"))
# 
# sip_periods_0 <- fread(x = file.path("Target_tables", "AUXILIAR",
#                          "sip_periods_0.csv"))

```

```{r}
# # add info of activations--------------------------------------------------
# path_origenes_consign <- file.path( "F:", "CERES2", "CONSIGN_SD2270",
#                                     "1-DATOS", "1-BRUTOS")
# 
# activations <- fread(file.path(path_origenes_consign, "01_SIP", "ext2", "V99",
#                 "BAJAS-REACTIVACIONES", "SD2270_SIP_SPO_4493_react_out.enc.txt"),
#                 header = TRUE) |>
#   clean_names() |>
#   rename(sip = nsip) |>
#   mutate(fecha = dmy(fecha)) |>
#   select(-v6) |>
#   # filter with the sample IDs
#   select(sip, fecha, accion)

```

```{r}
# # update observation periods-----------------------------------------------
# # there are some problematic sips that have more than one period
# # but they don't appear in the activation file: append them apart.
# problematic_sips <- sip_periods_0 |> 
#   filter(periodo > 1) |> 
#   distinct(sip) |> 
#   anti_join(activations) |> 
#   pull(sip)
# 
# # check problematic sips
# sip_periods_0 |> filter(sip %in% problematic_sips)
# activations |> filter(sip %in% problematic_sips)


```


```{r}
# # update observation periods-----------------------------------------------
# sip_periods_1 <- sip_periods_0 |> select(-fecha_defuncion) |>
#   filter(sip %nin% problematic_sips) |> 
#   left_join(activations,
#             join_by(sip, fecha_inicio <= fecha,
#                     fecha_fin >= fecha)) |> 
#   arrange(sip, fecha) |>
#   mutate(nueva_fecha_inicio = if_else(accion %in% c("Alta", "Reactivacion"),
#                                       fecha, NA_Date_),
#          nueva_fecha_fin = if_else(accion == "Baja", fecha, NA_Date_)) |>
#   group_by(sip) |> 
#    mutate(periodo = 1 + cumsum(as.numeric(lag(accion == "Baja", default = 0)))) |> 
#   group_by(sip, periodo) |>
#   summarise(fecha_inicio = max(fecha_inicio, nueva_fecha_inicio, na.rm = TRUE),
#          fecha_fin = min(fecha_fin, nueva_fecha_fin, na.rm = TRUE)) |>
#   ungroup() |>
#   arrange(sip)
# 
# sip_periods_2 <- sip_periods_0 |> select(-fecha_defuncion) |>
#   filter(sip %in% problematic_sips)
# 
# # all sip_periods
# sip_periods <- union(sip_periods_1, sip_periods_2)

```

```{r}
# # write table--------------------------------------------------------------
# fwrite(sip_periods, append = FALSE,
#        file = file.path("Target_tables", "AUXILIAR",
#                         "sip_periods.csv"))
# rm(sip_periods_0, sip_periods_1, sip_periods_2)

```

```{r}
# load table-----------------------------------------------------------------
sip_periods <- fread2(x = file.path("Target_tables", "AUXILIAR",
                        "sip_periods.csv"))

```

```{r}
# populate table-------------------------------------------------------------
from_sip_to_observation_period <- sip_periods |>
  select(sip,
         fecha_inicio,
         fecha_fin) |>
  transmute(
    observation_period_id = 1:n(),
    person_source_value = sip,
    observation_period_start_date = fecha_inicio,
    observation_period_end_date = fecha_fin,
    period_type_concept_id = 32828
  ) |> 
  left_join(person_ids, by = "person_source_value") |> 
  select(-person_source_value) |> 
  relocate(observation_period_id, person_id)
  

# write table----------------------------------------------------------------
fwrite(from_sip_to_observation_period, append = FALSE,
       file = file.path("Target_tables",
                        "observation_period_vid.csv"))

```

# death

## From sip to death

```{r}
# populate table-------------------------------------------------------------
from_sip_to_death <- from_sip_to_person |>
  select(person_id,
         fecha_defuncion) |>
  # retrieve only persons with a death date
  filter(!is.na(fecha_defuncion)) |> 
  # check duplicates
  tidylog::distinct() |> 
  transmute(person_id,
            death_date = fecha_defuncion,
            death_datetime = fecha_defuncion,
            death_type_concept_id = 32848,
            cause_concept_id = NA_integer_,
            cause_source_value = NA_character_,
            cause_source_concept_id = NA_integer_
            )

# write table----------------------------------------------------------------
fwrite(from_sip_to_death, append = FALSE,
       file = file.path("Target_tables",
                        "death_vid.csv"))

```

## From pmr to death

::: {.callout-important}
For now, it is not possible to perform the ETL process for the '**From pmr to death**' information. The sex of the newborn is currently unavailable, and in accordance with the OMOP conventions, these newborn records cannot be stored in the **person** table.
:::

```{r}
# populate table-------------------------------------------------------------
# from_pmr_to_death <- pmr

```

# Load source tables: part two

```{r}
# free up some memory--------------------------------------------------------
rm(sip, sip_periods, 
   from_sip_to_care_site, from_sip_to_care_site_write,
   from_sip_to_death, from_sip_to_observation_period, 
   from_sip_to_person, from_sip_to_person_write)

```

```{r}
# load tables----------------------------------------------------------------
# second part
pcv       <- fread(file.path(origin_tables, "pcv.csv"), encoding = "UTF-8")
cex       <- fread(file.path(origin_tables, "cex.csv"), encoding = "UTF-8")
aed       <- fread(file.path(origin_tables, "aed.csv"), encoding = "UTF-8")
diagnoses <- fread(file.path(origin_tables, "diagnoses.csv"), 
                    encoding = "UTF-8")
mdr       <- fread2(file.path(origin_tables, "mdr.csv"), encoding = "UTF-8")
eos       <- fread2(file.path(origin_tables, "eos.csv"),encoding = "UTF-8")

```

# visit_occurrence

## From pcv to visit_occurrence

```{r}
# populate table-------------------------------------------------------------
from_pcv_to_visit_occurrence <- pcv |>
  arrange(sip, fecha_consulta) |>
  # filter to ICD codes
  filter(tipo_codigo %in% c("ICD9CM", "ICD10ES")) |> 
  # create unique visit id---------------------------------------------------
  group_by(sip, fecha_consulta, serv_at_cod) |>
  mutate(visit_occurrence_id = cur_group_id()) |>
  ungroup() |> 
  transmute(
    visit_occurrence_id = visit_occurrence_id,
    person_source_value = sip,
    visit_concept_id = 9202,
    visit_start_date = fecha_consulta,
    visit_start_datetime = fecha_consulta,
    visit_end_date = fecha_consulta,
    visit_end_datetime = fecha_consulta,
    visit_type_concept_id = 32834,
    provider_id = NA_integer_,
    care_site_id = NA_integer_,
    visit_source_value = "PCV",
    visit_source_concept_id = 0,
    admitted_from_concept_id = 0,
    admitted_from_source_value = NA_character_,
    discharged_to_concept_id = 0,
    discharged_to_source_value = NA_character_,
    preceding_visit_occurrence_id = NA_integer_,
    diag_cod = diag_cod,
    tipo_codigo = tipo_codigo
    ) |>
  arrange(visit_occurrence_id) |> 
  left_join(person_ids, by = "person_source_value") |> 
  select(-person_source_value) |> 
  relocate(visit_occurrence_id, person_id)
  
# write table----------------------------------------------------------------
fwrite(from_pcv_to_visit_occurrence, append = FALSE,
       file = file.path("Target_tables", "AUXILIAR",
                        "from_pcv_to_visit_occurrence.csv"))

last_pcv_visit_occurrence_id <- max(from_pcv_to_visit_occurrence$visit_occurrence_id)

from_pcv_to_visit_occurrence_write <- from_pcv_to_visit_occurrence |> 
  select(-diag_cod, -tipo_codigo) |> 
  distinct()
  
# write table----------------------------------------------------------------
fwrite(from_pcv_to_visit_occurrence_write, append = FALSE,
       file = file.path("Target_tables", "AUXILIAR",
                        "visit_occurrence_vid_0.csv"))

```

## From cex to visit_occurrence

```{r}
# populate table-------------------------------------------------------------
from_cex_to_visit_occurrence <- cex |>
  # temporal fix -> move to cex_curation script
  filter(sip %in% sips_consign) |> 
  arrange(sip, fecha_consulta) |>
  # filter to ICD codes
  filter(
    tipo_codigo1 %in% c("ICD9CM", "ICD9ES") |
    tipo_codigo2 %in% c("ICD9CM", "ICD9ES") |
    tipo_codigo3 %in% c("ICD9CM", "ICD9ES") |
    tipo_codigo4 %in% c("ICD9CM", "ICD9ES")
      ) |> 
  # create unique visit id---------------------------------------------------
  transmute(
    visit_occurrence_id = 1:n() + last_pcv_visit_occurrence_id,
    person_source_value = sip,
    visit_concept_id = 9202,
    visit_start_date = fecha_consulta,
    visit_start_datetime = fecha_consulta,
    visit_end_date = fecha_consulta,
    visit_end_datetime = fecha_consulta,
    visit_type_concept_id = 32834,
    provider_id = NA_integer_,
    care_site_id = NA_integer_,
    visit_source_value = "CEX",
    visit_source_concept_id = 0,
    admitted_from_concept_id = 0,
    admitted_from_source_value = NA_character_,
    discharged_to_concept_id = 0,
    discharged_to_source_value = NA_character_,
    preceding_visit_occurrence_id = NA_integer_,
    d1_cod, d2_cod, d3_cod, d4_cod,
    tipo_codigo1, tipo_codigo2, tipo_codigo3, tipo_codigo4
    ) |> 
  arrange(visit_occurrence_id) |> 
  left_join(person_ids, by = "person_source_value") |> 
  select(-person_source_value) |> 
  relocate(visit_occurrence_id, person_id)

# write table----------------------------------------------------------------
fwrite(from_cex_to_visit_occurrence, append = FALSE,
       file = file.path("Target_tables", "AUXILIAR",
                        "from_cex_to_visit_occurrence.csv"))

last_cex_visit_occurrence_id <- max(from_cex_to_visit_occurrence$visit_occurrence_id)

from_cex_to_visit_occurrence_write <- from_cex_to_visit_occurrence |> 
  select(-d1_cod, -d2_cod, -d3_cod, -d4_cod,
         -tipo_codigo1, -tipo_codigo2, -tipo_codigo3, -tipo_codigo4) |> 
  distinct()
  
# write table----------------------------------------------------------------
fwrite(from_cex_to_visit_occurrence_write, append = TRUE,
       file = file.path("Target_tables", "AUXILIAR",
                        "visit_occurrence_vid_0.csv"))

```

## From mbds to visit_occurrence

```{r}
# populate table-------------------------------------------------------------
from_mbds_to_visit_occurrence <- mbds |>
  arrange(sip, fecha_ingreso) |>
  # fill care_site_id
  left_join(from_mbds_to_care_site |> 
    select(care_site_id, hosp_cod = care_site_source_value)) |> 
  # create unique visit id---------------------------------------------------
  transmute(
    visit_occurrence_id = 1:n() + last_cex_visit_occurrence_id,
    person_source_value = sip,
    visit_concept_id = 8717,
    visit_start_date = fecha_ingreso,
    visit_start_datetime = fecha_ingreso,
    visit_end_date = fecha_alta,
    visit_end_datetime = fecha_alta,
    visit_type_concept_id = 32824,
    provider_id = NA_integer_,
    care_site_id = care_site_id,
    visit_source_value = "MBDS",
    visit_source_concept_id = 0,
    admitted_from_concept_id = if_else(circ_ing_cod == 1,
                                       9203, 0),
    admitted_from_source_value = glue("{circ_ing_cod}: {circ_ing_desc}"),
    discharged_to_concept_id = case_when(
      circ_alta_cod == 7 ~ 38004279,
      circ_alta_cod == 8 ~ 38004277,
      circ_alta_cod == 9 ~ 8676,
      circ_alta_cod == 14 ~ 38004284,
      circ_alta_cod == 15 ~ 8717,
      circ_alta_cod == 17 ~ 9203,
      T ~ 0),
    discharged_to_source_value = glue("{circ_alta_cod}: {circ_alta_desc}"),
    preceding_visit_occurrence_id = NA_integer_,
    across(d1:p30),
    d_semana_gest,
    semana_gest,
    tipo_codigo
    ) |> 
  arrange(visit_occurrence_id) |> 
  left_join(person_ids, by = "person_source_value") |> 
  select(-person_source_value) |> 
  relocate(visit_occurrence_id, person_id)

# write table----------------------------------------------------------------
fwrite(from_mbds_to_visit_occurrence, append = FALSE,
       file = file.path("Target_tables", "AUXILIAR",
                        "from_mbds_to_visit_occurrence.csv"))

last_mbds_visit_occurrence_id <- max(from_mbds_to_visit_occurrence$visit_occurrence_id)

from_mbds_to_visit_occurrence_write <- from_mbds_to_visit_occurrence |> 
  select(-c(d1:p30, semana_gest, tipo_codigo, d_semana_gest)) |> 
  distinct()

# write table----------------------------------------------------------------
fwrite(from_mbds_to_visit_occurrence_write, append = TRUE,
       file = file.path("Target_tables", "AUXILIAR",
                        "visit_occurrence_vid_0.csv"))

```

## From aed to visit_occurrence

```{r}
# populate table-------------------------------------------------------------
from_aed_to_visit_occurrence <- aed |>
  arrange(sip, fecha_registro) |>
  # filter to ICD codes
  filter(
    tipo_codigo1 %in% c("ICD9CM", "ICD9ES") |
    tipo_codigo2 %in% c("ICD9CM", "ICD9ES")
      ) |> 
  # create unique visit id---------------------------------------------------
  transmute(
    visit_occurrence_id = 1:n() + last_mbds_visit_occurrence_id,
    person_source_value = sip,
    visit_concept_id = 9203,
    visit_start_date = fecha_registro,
    visit_start_datetime = fecha_registro,
    visit_end_date = fecha_alta,
    visit_end_datetime = fecha_alta,
    visit_type_concept_id = 32826,
    provider_id = NA_integer_,
    care_site_id = NA_integer_,
    visit_source_value = "AED",
    visit_source_concept_id = 0,
    admitted_from_concept_id = 0,
    admitted_from_source_value = NA_character_,
    discharged_to_concept_id = case_when(
      circ_alta_cod == 7 ~ 38004279,
      circ_alta_cod == 8 ~ 38004277,
      circ_alta_cod == 9 ~ 8676,
      circ_alta_cod == 14 ~ 38004284,
      circ_alta_cod == 15 ~ 8717,
      circ_alta_cod == 17 ~ 9203,
      T ~ 0),
    discharged_to_source_value = glue("{circ_alta_cod}: {circ_alta_desc}"),
    preceding_visit_occurrence_id = NA_integer_,
    diag_cod, diag2_cod,
    tipo_codigo1, tipo_codigo2
    ) |> 
  arrange(visit_occurrence_id) |> 
  left_join(person_ids, by = "person_source_value") |> 
  select(-person_source_value) |> 
  relocate(visit_occurrence_id, person_id)

# write table----------------------------------------------------------------
fwrite(from_aed_to_visit_occurrence, append = FALSE,
       file = file.path("Target_tables", "AUXILIAR",
                        "from_aed_to_visit_occurrence.csv"))

last_aed_visit_occurrence_id <- max(from_aed_to_visit_occurrence$visit_occurrence_id)

from_aed_to_visit_occurrence_write <- from_aed_to_visit_occurrence |> 
  select(-diag_cod, -diag2_cod,
         -tipo_codigo1, -tipo_codigo2) |> 
  distinct()
  
# write table----------------------------------------------------------------
fwrite(from_aed_to_visit_occurrence_write, append = TRUE,
       file = file.path("Target_tables", "AUXILIAR",
                        "visit_occurrence_vid_0.csv"))

```

## Fill preceding_visit_occurence_id

```{r}
# fill preceding_visit_occurrence_id-----------------------------------------
visit_occurrence_vid_0 <- fread(file.path("Target_tables", 
                          "AUXILIAR", "visit_occurrence_vid_0.csv"))

visit_occurrence_vid <- visit_occurrence_vid_0 |> 
  arrange(person_id, visit_start_date, visit_occurrence_id) |> 
  group_by(person_id) |> 
  mutate(preceding_visit_occurrence_id = lag(visit_occurrence_id)) |> 
  ungroup() |> 
  # trim discharged_to_source_value to fit omop specifications
  mutate(discharged_to_source_value = str_sub(discharged_to_source_value, 
                                              1, 50))

fwrite(visit_occurrence_vid, append = FALSE,
       file = file.path("Target_tables", "visit_occurrence_vid.csv"))

```

```{r}
# free up some memory--------------------------------------------------------
rm(visit_occurrence_vid, visit_occurrence_vid_0)

```


# condition_occurrence I (diagnoses)

## vocabularies

```{r}
# load concepts vocabulary---------------------------------------------------
concepts_vocabulary <- fread(file.path("Vocabularies", "CONCEPT.csv"))
concepts_relationship <- fread(file.path("Vocabularies", "CONCEPT_RELATIONSHIP.csv"))
concepts_ancestor <- fread(file.path("Vocabularies", "CONCEPT_ANCESTOR.csv"))

```

```{r}
# obtain standard concepts---------------------------------------------------
standards_concepts <- concepts_vocabulary |> 
  filter(standard_concept == "S") 

standard_concept_codes <- standards_concepts |> 
  distinct(concept_id) |> pull()

```


```{r}
# obtain icd9 concepts vocabulary--------------------------------------------
icd9_concepts <- concepts_vocabulary |> 
  filter(vocabulary_id == "ICD9CM")

icd9_concept_codes <- icd9_concepts |> 
  distinct(concept_id) |> pull()

concepts_relationship_icd9 <- concepts_relationship |> 
  filter(relationship_id == "Maps to") |> 
  filter(concept_id_1 %in% icd9_concept_codes)  |> 
  filter(concept_id_2 %in% standard_concept_codes) |>
  left_join(icd9_concepts |> 
              select(concept_code, concept_id_1 = concept_id)) |> 
  select(condition_concept_id = concept_id_2, 
         condition_source_concept_id = concept_id_1,
         condition_source_value = concept_code) |> 
  mutate(tipo_codigo = "ICD9CM")

```

```{r}
# obtain icd10 concepts vocabulary--------------------------------------------
icd10_concepts <- concepts_vocabulary |> 
  filter(vocabulary_id == "ICD10CM")

icd10_concept_codes <- icd10_concepts |> 
  distinct(concept_id) |> pull()

concepts_relationship_icd10 <- concepts_relationship |> 
  filter(relationship_id == "Maps to") |> 
  filter(concept_id_1 %in% icd10_concept_codes)  |> 
  filter(concept_id_2 %in% standard_concept_codes) |>
  left_join(icd10_concepts |> 
              select(concept_code, concept_id_1 = concept_id)) |> 
  select(condition_concept_id = concept_id_2, 
         condition_source_concept_id = concept_id_1,
         condition_source_value = concept_code) |> 
  mutate(tipo_codigo = "ICD10ES")

```

```{r}
# some detected bugs---------------------------------------------------------

# add relationships manually
# from pcv
icd9_concepts |> filter(concept_code == "E869.4")
icd10_concepts |> filter(concept_code == "C78.5")
icd10_concepts |> filter(concept_code == "C78.6")
icd10_concepts |> filter(concept_code == "C78.7")
icd10_concepts |> filter(concept_code == "C78.89")
icd10_concepts |> filter(concept_code == "C79.00")
icd10_concepts |> filter(concept_code == "C79.01")
icd10_concepts |> filter(concept_code == "C79.82")
icd10_concepts |> filter(concept_code == "O99.334")
icd10_concepts |> filter(concept_code == "Z72.0")
icd10_concepts |> filter(concept_code == "Z77.22")
# from mbds
icd10_concepts |> filter(concept_code == "C79.19")
icd10_concepts |> filter(concept_code == "Z57.31")
icd10_concepts |> filter(concept_code == "C79.02")


```
```{r}
# E869.4
concepts_relationship |> filter(concept_id_1 == 44834168)
# is a = 44830680 (E869)
concepts_vocabulary |> 
  filter(
    standard_concept == "S",
    str_detect(concept_name, "Smokeless tobacco user"))

manual_condition_relationship_0 <- tibble(
  condition_concept_id = 903666,
  condition_source_concept_id = 44834168,
  condition_source_value = "E869.4",
  tipo_codigo = "ICD9CM")

```

```{r}
# C78.5
concepts_relationship |> filter(concept_id_1 == 35206330)
# is a = 1567619 (C78)
concepts_vocabulary |> 
  filter(
    standard_concept == "S",
    str_detect(concept_name, "Secondary malignant neoplasm of large intestine"))

manual_condition_relationship_1 <- tibble(
  condition_concept_id = 200348,
  condition_source_concept_id = 35206330,
  condition_source_value = "C78.5",
  tipo_codigo = "ICD10ES")

```

```{r}
# C78.6
concepts_relationship |> filter(concept_id_1 == 35206331)
# is a = 1567619 (C78)
concepts_vocabulary |> 
  filter(
    standard_concept == "S",
    str_detect(concept_name, "Secondary malignant neoplasm of retroperitoneum and peritoneum"))

manual_condition_relationship_2 <- tibble(
  condition_concept_id = 196925,
  condition_source_concept_id = 35206331,
  condition_source_value = "C78.6",
  tipo_codigo = "ICD10ES")

```

```{r}
# C78.7
concepts_relationship |> filter(concept_id_1 == 35206332)
# is a = 1567619 (C78)
concepts_vocabulary |> 
  filter(
    standard_concept == "S",
    str_detect(concept_name, "Secondary malignant neoplasm of liver and intrahepatic bile duct"))

manual_condition_relationship_3 <- tibble(
  condition_concept_id = 44806773,
  condition_source_concept_id = 35206332,
  condition_source_value = "C78.7",
  tipo_codigo = "ICD10ES")

```

```{r}
# C78.89
concepts_relationship |> filter(concept_id_1 == 45576340)
# is a = 1567619 (C78), 1567622 (C78.8)
concepts_vocabulary |> 
  filter(concept_id == 1567619)

concepts_vocabulary |> 
  filter(
    standard_concept == "S",
    str_detect(concept_name, "Secondary malignant neoplasm of respiratory and digestive systems"))

manual_condition_relationship_4 <- tibble(
  condition_concept_id = 4147162,
  condition_source_concept_id = 45576340,
  condition_source_value = "C78.89",
  tipo_codigo = "ICD10ES")

```

```{r}
# C79.00
concepts_relationship |> filter(concept_id_1 == 45576341)
# is a = 1567624 (C79.0), 1567623 (C79)
concepts_vocabulary |> 
  filter(
    standard_concept == "S",
    str_detect(concept_name, "Secondary malignant neoplasm of renal pelvis"))

manual_condition_relationship_5 <- tibble(
  condition_concept_id = 4315670,
  condition_source_concept_id = 45576341,
  condition_source_value = "C79.00",
  tipo_codigo = "ICD10ES")

```

```{r}
# C79.01
concepts_relationship |> filter(concept_id_1 == 45552283)
# is a = 1567624 (C79.0), 1567623 (C79.01)
concepts_vocabulary |> 
  filter(
    standard_concept == "S",
    str_detect(concept_name, "Secondary malignant neoplasm of right kidney"))

manual_condition_relationship_6 <- tibble(
  condition_concept_id = 602668,
  condition_source_concept_id = 45552283,
  condition_source_value = "C79.01",
  tipo_codigo = "ICD10ES")

```

```{r}
# C79.82
concepts_relationship |> filter(concept_id_1 == 45600528)
# is a = 1567631 (C79.8), 1567623 (C79)
concepts_vocabulary |> 
  filter(
    standard_concept == "S",
    str_detect(concept_name, "Secondary malignant neoplasm of genital organ"))

manual_condition_relationship_7 <- tibble(
  condition_concept_id = 608735,
  condition_source_concept_id = 45600528,
  condition_source_value = "C79.82",
  tipo_codigo = "ICD10ES")

```

```{r}
# O99.334
concepts_relationship |> filter(concept_id_1 == 45534324)
# is a = 1571923 (O99), 1571931 (O99.3), 1571934 (O99.33)
concepts_relationship |> filter(concept_id_1 == 1571931) # we select this

concepts_vocabulary |> 
  filter(
    standard_concept == "S",
    str_detect(concept_name, "Disease of nervous system complicating pregnancy, childbirth and puerperium"))

manual_condition_relationship_8 <- tibble(
  condition_concept_id = 4063155,
  condition_source_concept_id = 45534324,
  condition_source_value = "O99.334",
  tipo_codigo = "ICD10ES")

```

```{r}
# Z72.0
concepts_relationship |> filter(concept_id_1 == 35225271)
# is a = 1576166 (Z72)
concepts_vocabulary |> 
  filter(
    standard_concept == "S",
    str_detect(concept_name, "Documentation that patient is a current tobacco user"))

manual_condition_relationship_9 <- tibble(
  condition_concept_id = 44786481,
  condition_source_concept_id = 35225271,
  condition_source_value = "Z72.0",
  tipo_codigo = "ICD10ES")

```

```{r}
# Z77.22
concepts_relationship |> filter(concept_id_1 == 45552107)
# is a = 1576177 (Z77), 1576185 (Z77.2)
concepts_vocabulary |> 
  filter(
    standard_concept == "S",
    str_detect(concept_name, "Exposure to potentially hazardous substance"))

manual_condition_relationship_10 <- tibble(
  condition_concept_id = 37016166,
  condition_source_concept_id = 45552107,
  condition_source_value = "Z77.22",
  tipo_codigo = "ICD10ES")

```

				

```{r}
# C79.19
concepts_relationship |> filter(concept_id_1 == 45537842)

concepts_vocabulary |> 
  filter(
    standard_concept == "S",
    str_detect(concept_name, "Secondary malignant neoplasm of urinary system"))

manual_condition_relationship_11 <- tibble(
  condition_concept_id = 78987,
  condition_source_concept_id = 45537842,
  condition_source_value = "C79.19",
  tipo_codigo = "ICD10ES")

```



```{r}
# Z57.31
concepts_relationship |> filter(concept_id_1 == 45537659)

concepts_vocabulary |> 
  filter(
    standard_concept == "S",
    str_detect(concept_name, "Setting of exposure to environmental or occupational hazard"))

manual_condition_relationship_12 <- tibble(
  condition_concept_id = 1002287,
  condition_source_concept_id = 45537659,
  condition_source_value = "Z57.31",
  tipo_codigo = "ICD10ES")

```

```{r}
# C79.02
concepts_relationship |> filter(concept_id_1 == 45600526)
# is a = 1567624 (C79.0), 1567623 (C79.01)
concepts_vocabulary |> 
  filter(
    standard_concept == "S",
    str_detect(concept_name, "Secondary malignant neoplasm of left kidney"))

manual_condition_relationship_13 <- tibble(
  condition_concept_id = 605437,
  condition_source_concept_id = 45600526,
  condition_source_value = "C79.02",
  tipo_codigo = "ICD10ES")

```

```{r}
# une manual_condition_relationship------------------------------------------
manual_condition_relationship <- manual_condition_relationship_0 |> 
  union(manual_condition_relationship_1) |> 
  union(manual_condition_relationship_2) |> 
  union(manual_condition_relationship_3) |> 
  union(manual_condition_relationship_4) |> 
  union(manual_condition_relationship_5) |> 
  union(manual_condition_relationship_6) |> 
  union(manual_condition_relationship_7) |> 
  union(manual_condition_relationship_8) |> 
  union(manual_condition_relationship_9) |> 
  union(manual_condition_relationship_10) |>  
  union(manual_condition_relationship_11) |> 
  union(manual_condition_relationship_12) |> 
  union(manual_condition_relationship_13) 

```


```{r}
# union icd9 and icd10 concepts_relationship---------------------------------
concepts_relationship_icd9_icd10 <- concepts_relationship_icd9 |> 
  union(concepts_relationship_icd10) |> 
  union(manual_condition_relationship)

fwrite(concepts_relationship_icd9_icd10, file.path("Target_tables", 
                  "AUXILIAR", "concepts_relationship_icd9_icd10.csv"))

```

## From pcv to condition_occurrence

```{r}
# populate table-------------------------------------------------------------
from_pcv_to_condition_occurrence_0 <- from_pcv_to_visit_occurrence |>
  # check duplicates
  tidylog::distinct() |>
  transmute(
    person_id,
    # condition_concept_id = "map",
    condition_start_date = visit_start_date,
    condition_start_datetime = visit_start_date,
    condition_end_date = NA_Date_,
    condition_end_datetime = NA_Date_,
    condition_type_concept_id = 32834,
    condition_status_concept_id = 32893,
    stop_reason = NA_character_,
    provider_id = NA_integer_,
    visit_occurrence_id = visit_occurrence_id,
    visit_detail_id = NA_integer_,
    condition_source_value = diag_cod,
    # condition_source_concept_id = "map",
    condition_status_source_value = "PCV",
    tipo_codigo
    ) |> 
  # temporal fix -> change in pcv curation script
  mutate(tipo_codigo = if_else(
    condition_source_value == "E869.4", "ICD9CM", tipo_codigo
  ))

from_pcv_to_condition_occurrence_0 |> filter(
  condition_source_value == "E869.4"
)

```

```{r}
# pcv codes------------------------------------------------------------------
from_pcv_to_condition_occurrence <- from_pcv_to_condition_occurrence_0 |>
  left_join(concepts_relationship_icd9_icd10, 
            by = c("condition_source_value", "tipo_codigo")) |> 
  mutate(condition_occurrence_id = 1:n()) |> 
  relocate(
    condition_occurrence_id,
    person_id,
    condition_concept_id,
    condition_start_date,
    condition_start_datetime,
    condition_end_date,
    condition_end_datetime,
    condition_type_concept_id,
    condition_status_concept_id,
    stop_reason,
    provider_id,
    visit_occurrence_id,
    visit_detail_id,
    condition_source_value,
    condition_source_concept_id,
    condition_status_source_value
  )

# check
from_pcv_to_condition_occurrence |> 
  filter(is.na(condition_source_concept_id)) |> 
  distinct(condition_source_value)
# All is mapped --> OK

```

```{r}
# write table----------------------------------------------------------------
fwrite(from_pcv_to_condition_occurrence, append = FALSE,
       file = file.path("Target_tables", "AUXILIAR",
                        "from_pcv_to_condition_occurrence.csv"))

last_pcv_condition_occurrence_id <- 
  max(from_pcv_to_condition_occurrence$condition_occurrence_id)

from_pcv_to_condition_occurrence_write <- from_pcv_to_condition_occurrence |> 
  select(-tipo_codigo)

fwrite(from_pcv_to_condition_occurrence_write, append = FALSE,
       file = file.path("Target_tables",
                        "condition_occurrence_vid.csv"))

```

## From cex to condition_occurrence

```{r}
# populate table-------------------------------------------------------------
from_cex_to_condition_occurrence_0 <- from_cex_to_visit_occurrence |>
  # check duplicates
  tidylog::distinct() |>
  # pivot_longer
  mutate(
    d1_cod_tipo = str_c(d1_cod, tipo_codigo1, sep = "|"),
    d2_cod_tipo = str_c(d2_cod, tipo_codigo2, sep = "|"),
    d3_cod_tipo = str_c(d3_cod, tipo_codigo3, sep = "|"),
    d4_cod_tipo = str_c(d4_cod, tipo_codigo4, sep = "|")) |>
    select(-c(d1_cod, d2_cod, d3_cod, d4_cod,
              tipo_codigo1, tipo_codigo2, tipo_codigo3, tipo_codigo4)) |> 
  pivot_longer(d1_cod_tipo:d4_cod_tipo,
               values_to = c("diag_cod_tipo")) |> 
  select(-name) |> 
  separate(diag_cod_tipo, into = c("diag_cod", "tipo_codigo"), sep ="\\|") |> 
  filter(tipo_codigo %in% c("ICD9CM", "ICD10ES")) |> 
  transmute(
    person_id = person_id,
    # condition_concept_id = "map",
    condition_start_date = visit_start_date,
    condition_start_datetime = visit_start_date,
    condition_end_date = NA_Date_,
    condition_end_datetime = NA_Date_,
    condition_type_concept_id = 32834,
    condition_status_concept_id = 32893,
    stop_reason = NA_character_,
    provider_id = NA_integer_,
    visit_occurrence_id = visit_occurrence_id,
    visit_detail_id = NA_integer_,
    condition_source_value = diag_cod,
    # condition_source_concept_id = "map",
    condition_status_source_value = "CEX",
    tipo_codigo
    )

```

```{r}
# cex codes------------------------------------------------------------------
from_cex_to_condition_occurrence <- from_cex_to_condition_occurrence_0 |>
  left_join(concepts_relationship_icd9_icd10, 
            by = c("condition_source_value", "tipo_codigo")) |> 
  mutate(condition_occurrence_id = 1:n() + last_pcv_condition_occurrence_id) |> 
  relocate(
    condition_occurrence_id,
    person_id,
    condition_concept_id,
    condition_start_date,
    condition_start_datetime,
    condition_end_date,
    condition_end_datetime,
    condition_type_concept_id,
    condition_status_concept_id,
    stop_reason,
    provider_id,
    visit_occurrence_id,
    visit_detail_id,
    condition_source_value,
    condition_source_concept_id,
    condition_status_source_value
  )

# check
from_cex_to_condition_occurrence |> 
  filter(is.na(condition_source_concept_id)) 
# All is mapped --> OK

```

```{r}
# write table----------------------------------------------------------------
fwrite(from_cex_to_condition_occurrence, append = FALSE,
       file = file.path("Target_tables", "AUXILIAR",
                        "from_cex_to_condition_occurrence.csv"))

last_cex_condition_occurrence_id <- 
  max(from_cex_to_condition_occurrence$condition_occurrence_id)

from_cex_to_condition_occurrence_write <- from_cex_to_condition_occurrence |> 
  select(-tipo_codigo)

fwrite(from_cex_to_condition_occurrence_write, append = TRUE,
       file = file.path("Target_tables",
                        "condition_occurrence_vid.csv"))

```

## From mbds to condition_occurrence

```{r}
# populate table-------------------------------------------------------------
from_mbds_to_condition_occurrence_0 <- from_mbds_to_visit_occurrence |>
  # check duplicates
  tidylog::distinct() |>
  # pivot_longer
  pivot_longer(d1:d30,
               values_to = c("diag_cod")) |> 
  filter(tipo_codigo %in% c("ICD9CM", "ICD10ES")) |> 
  # remove empty diagnoses
  tidylog::filter(!is.na(diag_cod), diag_cod %nin% c("", "-")) |>   
  transmute(
    person_id,
    # condition_concept_id = "map",
    condition_start_date = visit_start_date,
    condition_start_datetime = visit_start_date,
    condition_end_date = NA_Date_,
    condition_end_datetime = NA_Date_,
    condition_type_concept_id = 32824,
    condition_status_concept_id = if_else(name == "d1", 32903, 32909),
    stop_reason = NA_character_,
    provider_id = NA_integer_,
    visit_occurrence_id = visit_occurrence_id,
    visit_detail_id = NA_integer_,
    condition_source_value = diag_cod,
    # condition_source_concept_id = "map",
    condition_status_source_value = "MBDS",
    tipo_codigo
    )

```

```{r}
# mbds codes------------------------------------------------------------------
from_mbds_to_condition_occurrence <- from_mbds_to_condition_occurrence_0 |>
  left_join(concepts_relationship_icd9_icd10, 
            by = c("condition_source_value", "tipo_codigo")) |> 
  mutate(condition_occurrence_id = 1:n() + last_cex_condition_occurrence_id) |> 
  relocate(
    condition_occurrence_id,
    person_id,
    condition_concept_id,
    condition_start_date,
    condition_start_datetime,
    condition_end_date,
    condition_end_datetime,
    condition_type_concept_id,
    condition_status_concept_id,
    stop_reason,
    provider_id,
    visit_occurrence_id,
    visit_detail_id,
    condition_source_value,
    condition_source_concept_id,
    condition_status_source_value
  )

# check
from_mbds_to_condition_occurrence |> 
  filter(is.na(condition_source_concept_id)) |> 
  distinct(condition_source_value) |> 
  arrange(condition_source_value)
# Some weird codes -> map to 0


```

```{r}
# write table----------------------------------------------------------------
fwrite(from_mbds_to_condition_occurrence, append = FALSE,
       file = file.path("Target_tables", "AUXILIAR",
                        "from_mbds_to_condition_occurrence.csv"))

last_mbds_condition_occurrence_id <- 
  max(from_mbds_to_condition_occurrence$condition_occurrence_id)

from_mbds_to_condition_occurrence_write <- from_mbds_to_condition_occurrence |> 
  select(-tipo_codigo) |> 
  mutate(condition_concept_id = if_else(is.na(condition_concept_id), 
                                        0, condition_concept_id))

fwrite(from_mbds_to_condition_occurrence_write, append = TRUE,
       file = file.path("Target_tables",
                        "condition_occurrence_vid.csv"))

```

## From aed to condition_occurrence

```{r}
# populate table-------------------------------------------------------------
from_aed_to_condition_occurrence_0 <- from_aed_to_visit_occurrence |>
  # check duplicates
  tidylog::distinct() |>
  # pivot_longer
  mutate(
    d1_cod_tipo = str_c(diag_cod, tipo_codigo1, sep = "|"),
    d2_cod_tipo = str_c(diag2_cod, tipo_codigo2, sep = "|")) |>
    select(-c(diag_cod, diag2_cod, 
              tipo_codigo1, tipo_codigo2)) |> 
  pivot_longer(d1_cod_tipo:d2_cod_tipo,
               values_to = c("diag_cod_tipo")) |> 
  select(-name) |> 
  separate(diag_cod_tipo, into = c("diag_cod", "tipo_codigo"), sep ="\\|") |> 
  filter(tipo_codigo %in% c("ICD9CM", "ICD10ES")) |> 
  transmute(
    person_id,
    # condition_concept_id = "map",
    condition_start_date = visit_start_date,
    condition_start_datetime = visit_start_date,
    condition_end_date = NA_Date_,
    condition_end_datetime = NA_Date_,
    condition_type_concept_id = 32826,
    condition_status_concept_id = 32893,
    stop_reason = NA_character_,
    provider_id = NA_integer_,
    visit_occurrence_id = visit_occurrence_id,
    visit_detail_id = NA_integer_,
    condition_source_value = diag_cod,
    # condition_source_concept_id = "map",
    condition_status_source_value = "AED",
    tipo_codigo
    )

```

```{r}
# aed codes------------------------------------------------------------------
from_aed_to_condition_occurrence <- from_aed_to_condition_occurrence_0 |>
  left_join(concepts_relationship_icd9_icd10, 
            by = c("condition_source_value", "tipo_codigo")) |> 
  mutate(condition_occurrence_id = 1:n() + last_mbds_condition_occurrence_id) |> 
  relocate(
    condition_occurrence_id,
    person_id,
    condition_concept_id,
    condition_start_date,
    condition_start_datetime,
    condition_end_date,
    condition_end_datetime,
    condition_type_concept_id,
    condition_status_concept_id,
    stop_reason,
    provider_id,
    visit_occurrence_id,
    visit_detail_id,
    condition_source_value,
    condition_source_concept_id,
    condition_status_source_value
  )

# check
from_aed_to_condition_occurrence |> 
  filter(is.na(condition_source_concept_id)) 
# All is mapped --> OK

```

```{r}
# write table----------------------------------------------------------------
fwrite(from_aed_to_condition_occurrence, append = FALSE,
       file = file.path("Target_tables", "AUXILIAR",
                        "from_aed_to_condition_occurrence.csv"))

last_aed_condition_occurrence_id <- 
  max(from_aed_to_condition_occurrence$condition_occurrence_id)

from_aed_to_condition_occurrence_write <- from_aed_to_condition_occurrence |> 
  select(-tipo_codigo)

fwrite(from_aed_to_condition_occurrence_write, append = TRUE,
       file = file.path("Target_tables",
                        "condition_occurrence_vid.csv"))

```

## From diagnoses to condition_occurrence

```{r}
# populate table-------------------------------------------------------------
from_diagnoses_to_condition_occurrence_0 <- diagnoses |>
  # temporal fix -> move to curation script
  filter(sip %in% sips_consign) |> 
  # check duplicates
  tidylog::distinct() |>
  filter(tipo_codigo %in% c("ICD9CM", "ICD10ES")) |> 
  transmute(
    person_source_value = sip,
    # condition_concept_id = "map",
    condition_start_date = fecha_act,
    condition_start_datetime = fecha_act,
    condition_end_date = fecha_desact,
    condition_end_datetime = fecha_desact,
    condition_type_concept_id = 32817,
    condition_status_concept_id = 32893,
    stop_reason = NA_character_,
    provider_id = NA_integer_,
    visit_occurrence_id = NA_integer_,
    visit_detail_id = NA_integer_,
    condition_source_value = diag_cod,
    # condition_source_concept_id = "map",
    condition_status_source_value = "DIAGNOSES",
    tipo_codigo
    ) |> 
  left_join(person_ids, by = "person_source_value") |> 
  select(-person_source_value) |> 
  relocate(visit_occurrence_id, person_id)

```

```{r}
# diagnoses codes------------------------------------------------------------
from_diagnoses_to_condition_occurrence <- from_diagnoses_to_condition_occurrence_0 |>
  left_join(concepts_relationship_icd9_icd10, 
            by = c("condition_source_value", "tipo_codigo")) |> 
  mutate(condition_occurrence_id = 1:n() + last_aed_condition_occurrence_id) |> 
  relocate(
    condition_occurrence_id,
    person_id,
    condition_concept_id,
    condition_start_date,
    condition_start_datetime,
    condition_end_date,
    condition_end_datetime,
    condition_type_concept_id,
    condition_status_concept_id,
    stop_reason,
    provider_id,
    visit_occurrence_id,
    visit_detail_id,
    condition_source_value,
    condition_source_concept_id,
    condition_status_source_value
  )

# check
from_diagnoses_to_condition_occurrence |> 
  filter(is.na(condition_source_concept_id)) 
# All is mapped --> OK

```

```{r}
# write table----------------------------------------------------------------
fwrite(from_diagnoses_to_condition_occurrence, append = FALSE,
       file = file.path("Target_tables", "AUXILIAR",
                        "from_diagnoses_to_condition_occurrence.csv"))

last_diagnoses_condition_occurrence_id <- 
  max(from_diagnoses_to_condition_occurrence$condition_occurrence_id)

from_diagnoses_to_condition_occurrence_write <- from_diagnoses_to_condition_occurrence |> 
  select(-tipo_codigo)

fwrite(from_diagnoses_to_condition_occurrence_write, append = TRUE,
       file = file.path("Target_tables",
                        "condition_occurrence_vid.csv"))

```

# condition_occurrence II (pregnancy eras)

## vocabularies

```{r}
# look concepts--------------------------------------------------------------
concepts_vocabulary |> filter(domain_id == "Type Concept",
                              standard_concept == "S") 
concepts_vocabulary |> filter(domain_id == "Condition Status") 
  
concepts_vocabulary |> filter(standard_concept == "S") |> 
  filter(str_detect(concept_name, "Pregnancy")) 
  
```

## From mdr to condition_occurrence

```{r}
# populate table-------------------------------------------------------------
from_mdr_to_condition_occurrence <- mdr |>
  # temporal fix -> move to curation script
  filter(sip_madre %in% sips_consign) |>
  transmute(
    condition_occurrence_id = 1:n() + last_diagnoses_condition_occurrence_id,
    person_source_value = sip_madre,
    # 4142469: Pregnancy time period; 4128331: Pregnancy;
    # 4336958: Term pregnancy; 
    condition_concept_id = 4336958,
    # when semana_gest is missing a value of 38 weeks is imputed
    condition_start_date = if_else(!is.na(semana_gest),
      fecha_nac_hijo %m-% weeks(semana_gest),
      fecha_nac_hijo %m-% weeks(38)),    
    condition_start_datetime = condition_start_date,
    condition_end_date = fecha_nac_hijo,
    condition_end_datetime = condition_end_date,
    # 32879: Registry
    condition_type_concept_id = 32879,
    # 32906: Resolved condition	
    condition_status_concept_id = 32906,
    stop_reason = "livebirth",
    provider_id = NA_integer_,
    visit_occurrence_id = NA_integer_,
    visit_detail_id = NA_integer_,
    condition_source_value = NA_character_,
    condition_source_concept_id = NA_integer_,
    condition_status_source_value = "MDR"
    ) |> 
  left_join(person_ids, by = "person_source_value") |> 
  select(-person_source_value) |> 
relocate(
    condition_occurrence_id,
    person_id,
    condition_concept_id,
    condition_start_date,
    condition_start_datetime,
    condition_end_date,
    condition_end_datetime,
    condition_type_concept_id,
    condition_status_concept_id,
    stop_reason,
    provider_id,
    visit_occurrence_id,
    visit_detail_id,
    condition_source_value,
    condition_source_concept_id,
    condition_status_source_value) |> 
  # check duplicates
  tidylog::distinct()

```

```{r}
# write table----------------------------------------------------------------
fwrite(from_mdr_to_condition_occurrence, append = FALSE,
       file = file.path("Target_tables", "AUXILIAR",
                        "from_mdr_to_condition_occurrence.csv"))

last_mdr_condition_occurrence_id <- 
  max(from_mdr_to_condition_occurrence$condition_occurrence_id)

fwrite(from_mdr_to_condition_occurrence, append = TRUE,
       file = file.path("Target_tables",
                        "condition_occurrence_vid.csv"))

```

## From eos to condition_occurrence

```{r}
# populate table-------------------------------------------------------------
from_eos_to_condition_occurrence <- eos |>
  # temporal fix -> move to curation script
  filter(sip %in% sips_consign) |>
  # fix resultado_rn2, resultado_rn3
  mutate(resultado_rn2 = if_else(resultado_rn2 == "", 
                                 NA_character_, resultado_rn2),
         resultado_rn3 = if_else(resultado_rn3 == "", 
                                 NA_character_, resultado_rn3)) |> 
  # check duplicates
  tidylog::distinct() |>
  transmute(
    condition_occurrence_id = 1:n() + last_mdr_condition_occurrence_id,
    person_source_value = sip,
    # 4142469: Pregnancy time period; 4128331: Pregnancy;
    # 4336958: Term pregnancy; 
    condition_concept_id = 4142469,
    # when semana_gest is missing the observation is removed
    condition_start_date = fecha_fin_emb %m-% weeks(semana_gest),
    condition_start_datetime = condition_start_date,
    condition_end_date = fecha_fin_emb,
    condition_end_datetime = condition_end_date,
    # 32879: Registry; 32817: EHR;
    condition_type_concept_id = 32817,
    # 32906: Resolved condition	
    condition_status_concept_id = 32906,
    stop_reason = "End of pregnancy",
    provider_id = NA_integer_,
    visit_occurrence_id = NA_integer_,
    visit_detail_id = NA_integer_,
    condition_source_value = glue("{multiple_pregnancy}: {resultado_rn1}/{resultado_rn2}/{resultado_rn3}"),
    condition_source_concept_id = NA_integer_,
    condition_status_source_value = "EOS"
    )  |> 
  left_join(person_ids, by = "person_source_value") |> 
  select(-person_source_value) |> 
  relocate(condition_occurrence_id, person_id) |> 
  tidylog::filter(!is.na(condition_start_date))

```

```{r}
# write table----------------------------------------------------------------
fwrite(from_eos_to_condition_occurrence, append = FALSE,
       file = file.path("Target_tables", "AUXILIAR",
                        "from_eos_to_condition_occurrence.csv"))

last_eos_condition_occurrence_id <- 
  max(from_eos_to_condition_occurrence$condition_occurrence_id)

fwrite(from_eos_to_condition_occurrence, append = TRUE,
       file = file.path("Target_tables",
                        "condition_occurrence_vid.csv"))

```

# procedure_occurrence 

## vocabularies

```{r}
# obtain icd9 concepts vocabulary--------------------------------------------
icd9_procedures <- concepts_vocabulary |> 
  filter(vocabulary_id == "ICD9Proc")

icd9_procedure_codes <- icd9_procedures |> 
  distinct(concept_id) |> pull()

concepts_relationship_icd9_proc <- concepts_relationship |> 
  filter(relationship_id == "Maps to") |> 
  filter(concept_id_1 %in% icd9_procedure_codes)  |> 
  filter(concept_id_2 %in% standard_concept_codes) |>
  left_join(icd9_procedures |> 
              select(concept_code, concept_id_1 = concept_id)) |> 
  select(procedure_concept_id = concept_id_2, 
         procedure_source_concept_id = concept_id_1,
         procedure_source_value = concept_code) |> 
  mutate(tipo_codigo = "ICD9CM")

```


```{r}
# obtain icd10 concepts vocabulary--------------------------------------------
icd10_procedures <- concepts_vocabulary |> 
  filter(vocabulary_id == "ICD10PCS")

concepts_vocabulary |> distinct(vocabulary_id)

icd10_procedure_codes <- icd10_procedures |> 
  distinct(concept_id) |> pull()

concepts_relationship_icd10_proc <- concepts_relationship |> 
  filter(relationship_id == "Maps to") |> 
  filter(concept_id_1 %in% icd10_procedure_codes)  |> 
  filter(concept_id_2 %in% standard_concept_codes) |>
  left_join(icd10_procedures |> 
              select(concept_code, concept_id_1 = concept_id)) |> 
  select(procedure_concept_id = concept_id_2, 
         procedure_source_concept_id = concept_id_1,
         procedure_source_value = concept_code) |> 
  mutate(tipo_codigo = "ICD10ES")

```


```{r}
# union icd9 and icd10 concepts_relationship---------------------------------
concepts_relationship_icd9_icd10_proc <- concepts_relationship_icd9_proc |> 
  union(concepts_relationship_icd10_proc)

```

## From mbds to procedure_occurrence

```{r}
# populate table-------------------------------------------------------------
from_mbds_to_procedure_occurrence_0 <- from_mbds_to_visit_occurrence |>
  # check duplicates
  tidylog::distinct() |>
  # pivot_longer
  pivot_longer(p1:p30,
               values_to = c("proc_cod")) |> 
  filter(tipo_codigo %in% c("ICD9CM", "ICD10ES")) |> 
  # remove empty procedures
  tidylog::filter(!is.na(proc_cod), proc_cod %nin% c("", "-")) |> 
  transmute(
    person_id,
    # procedure_concept_id = "map",
    procedure_date = visit_start_date,
    procedure_datetime = visit_start_date,
    procedure_end_date = visit_end_date,
    procedure_end_datetime = visit_end_date,
    procedure_type_concept_id = 32824,
    modifier_concept_id = 0,
    quantity = 1,
    provider_id = NA_integer_,
    visit_occurrence_id = visit_occurrence_id,
    visit_detail_id = NA_integer_,
    procedure_source_value = proc_cod,
    # procedure_source_concept_id = "map",
    modifier_source_value = "MBDS",
    tipo_codigo
    )

```

```{r}
# mbds codes------------------------------------------------------------------
from_mbds_to_procedure_occurrence <- from_mbds_to_procedure_occurrence_0 |>
  left_join(concepts_relationship_icd9_icd10_proc, 
            by = c("procedure_source_value", "tipo_codigo")) |> 
  mutate(procedure_occurrence_id = 1:n()) |> 
  relocate(
    procedure_occurrence_id,
    person_id,
    procedure_concept_id,
    procedure_date,
    procedure_datetime,
    procedure_end_date,
    procedure_end_datetime,
    procedure_type_concept_id,
    modifier_concept_id,
    quantity,
    provider_id,
    visit_occurrence_id,
    visit_detail_id,
    procedure_source_value,
    procedure_source_concept_id,
    modifier_source_value
  )

# check
from_mbds_to_procedure_occurrence |> 
  filter(is.na(procedure_source_concept_id)) 
# All is mapped --> OK

```

```{r}
# write table----------------------------------------------------------------
fwrite(from_mbds_to_procedure_occurrence, append = FALSE,
       file = file.path("Target_tables", "AUXILIAR",
                        "from_mbds_to_procedure_occurrence.csv"))

last_mbds_procedure_occurrence_id <- 
  max(from_mbds_to_procedure_occurrence$procedure_occurrence_id)

from_mbds_to_procedure_occurrence_write <- from_mbds_to_procedure_occurrence |> 
  select(-tipo_codigo)

fwrite(from_mbds_to_procedure_occurrence_write, append = FALSE,
       file = file.path("Target_tables",
                        "procedure_occurrence_vid.csv"))

```

# Load source tables: part three

```{r}
# free up some memory--------------------------------------------------------
rm(pcv, from_pcv_to_condition_occurrence, from_pcv_to_condition_occurrence_0,
   from_pcv_to_condition_occurrence_write, from_pcv_to_visit_occurrence,
   from_pcv_to_visit_occurrence_write)

rm(diagnoses, from_diagnoses_to_condition_occurrence, 
   from_diagnoses_to_condition_occurrence_0,
   from_diagnoses_to_condition_occurrence_write)

rm(from_mbds_to_condition_occurrence, 
   from_mbds_to_condition_occurrence_0,
   from_mbds_to_condition_occurrence_write)

rm(cex, from_cex_to_condition_occurrence,
   from_cex_to_condition_occurrence_0,
   from_cex_to_condition_occurrence_write
   )

rm(aed, from_aed_to_condition_occurrence,
   from_aed_to_condition_occurrence_0,
   from_aed_to_condition_occurrence_write
   )

rm(from_mbds_to_procedure_occurrence, 
   from_mbds_to_procedure_occurrence_0,
   from_mbds_to_procedure_occurrence_write,
   from_mbds_to_visit_occurrence,
   from_mbds_to_visit_occurrence_write)

gc()

```


```{r}
# load tables----------------------------------------------------------------
# third part
gaia      <- fread(file.path(origin_tables, "gaia.csv"), encoding = "Latin-1")
siv       <- fread(file.path(origin_tables, "siv.csv"), encoding = "UTF-8")
redmiva   <- fread(file.path(origin_tables, "redmiva.csv"), encoding = "UTF-8")

```

# drug_exposure

## vocabularies

```{r}
# load gaia_clinical_drugs---------------------------------------------------
gaia_clinical_drugs5 <- fread(file.path("..", "Consign", "Resultados",
                               "gaia_masters", "gaia_clinical_drugs5.csv"),
                               encoding = "Latin-1")

```

```{r}
# check gaia_master----------------------------------------------------------
gaia_clinical_drugs5 |> distinct(atc_cod, atc_desc)

gaia_clinical_drugs5 |> distinct(via_cod, via_desc) |> 
  arrange(via_desc)

```

The route mapping is made one by one. Checking the *via_desc* and selecting the approppiate standard route *concept_id*. 

```{r}
# route_mapping--------------------------------------------------------------
gaia_clinical_drugs5 |> distinct(via_cod, via_desc) |> 
  arrange(via_desc) 

standard_route_concepts <- concepts_vocabulary |> 
  filter(domain_id == "Route") |> 
  filter(standard_concept == "S") |> 
  arrange(concept_name)

standard_route_concepts |> filter(str_detect(concept_name, "arti"))

gaia_clinical_drugs5 |> distinct(via_cod, via_desc) |> 
  arrange(via_desc) |> pull(via_desc)

concepts_relationship_route_0 <- gaia_clinical_drugs5 |> distinct(via_cod, via_desc) |> 
  arrange(via_desc)  |> 
  mutate(concept_name = c(
    # "BUCAL"
    "Buccal route",
    # "BUCOFARINGEA"
    "Oropharyngeal route",
    # "INHALATORIA/PULMONAR" 
    "Inhalation",
    # "INTRADERMICA"        
    "Intradermal route",
    # "INTRAMUSCULAR"    
    "Intramuscular route",
    # "INTRARTICULAR"       
    "Intra-articular route",
    # "INTRAVENOSA"     
    "Intravenous route",
    # "INTRAVESICAL"  
    "Intravesical route",
    # "INTRAVITREA"
    "Intravitreal route",
    # "NASAL"  
    "Nasal route",
    # "OFTALMICA"  
    "Ocular route",
    # "ORAL"               
    "Oral route",
    # "OTICA"                
    "Otic route",
    # "PARENTERAL"           
    "Subcutaneous route",
    # "PERCUTANEA/PARCHES"  
    "Percutaneous route",
    # "PULMONAR"             
    "Respiratory tract route",
    # "RECTAL"      
    "Rectal route",
    # "RECTAL"      
    "Rectal route",
    # "SUBCUTANEA"          
    "Subcutaneous route",
    # "SUBCUTANEA"          
    "Subcutaneous route",
    # "SUBLINGUAL"           
    "Sublingual route",
    # "TOPICA DERMICA"
    "Topical route",
    # "TRANSDERMAL"
    "Transdermal route"
  )) 

concepts_relationship_route <- concepts_relationship_route_0 |> 
  left_join(standard_route_concepts |> 
              select(route_concept_id = concept_id, 
                     concept_name)) |> 
  distinct(route_concept_id,
           route_source_value = via_desc)

fwrite(concepts_relationship_route, file.path("Target_tables", 
                  "AUXILIAR", "concepts_relationship_route.csv"))

```



```{r}
# gaia drug_concept_id (atc level) mapping-----------------------------------
atc_concepts <- concepts_vocabulary |> 
  filter(concept_code %in% (gaia_clinical_drugs5 |> 
                              distinct(atc_cod) |>  pull()))

atc_concept_codes <- atc_concepts |> 
  distinct(concept_id) |> pull()

missing_presentations <- gaia_clinical_drugs5 |> 
 anti_join(atc_concepts, by = c(atc_cod = "concept_code")) 

missing_atc_cod_desc <- missing_presentations |> 
  distinct(atc_cod, atc_desc) |> 
  arrange(atc_cod)

missing_atc_source_codes <- missing_atc_cod_desc |> pull(atc_cod)

```


```{r}
# search manually atc unmaped codes------------------------------------------
unmpaded_atc_codes_to_standard <- standards_concepts |> 
  # "A10BB91" GLISENTIDA
  filter(concept_class_id == "Ingredient",
  str_detect(concept_name, "GLISENTIDE")) |> union(
# "C01BA92" HIDROQUINIDINA
standards_concepts |> filter(concept_class_id == "Ingredient",
  str_detect(concept_name, "hydroquinidine"))) |> union(
# "C01BB91" FENITOINA
standards_concepts |> filter(concept_class_id == "Ingredient",
  str_detect(concept_name, "^phenytoin"))) |> union(
# "C03XW91" UREA
standards_concepts |> filter(concept_class_id == "Ingredient",
  str_detect(concept_name, "^urea$"))) |> union(
# "C04AX57" VINCAMINA, COMBINACIONES CON	
standards_concepts |> filter(concept_class_id == "Ingredient",
  str_detect(concept_name, "vincamine"))) |> union(
# "J05AC91" AMANTADINA
standards_concepts |> filter(concept_class_id == "Ingredient",
  str_detect(concept_name, "amantadine"))) |> union(
# "L03AX91" FOSFOGLICOPEPTICAL
standards_concepts |> filter(
  str_detect(concept_name, "^Glycopeptide$"))) |> union(
# "M01AX93" ISONIXINA
standards_concepts |> filter(concept_class_id == "Ingredient",
  str_detect(concept_name, "^isoniazid"))) |> union(
# "M01BA92" INDOMETACINA Y PREDNISONA, COMBINACIONES CON	
standards_concepts |> filter(concept_class_id == "Ingredient",
  str_detect(concept_name, "^indomethacin"))) |> union(
# "N02BG91" CLONIXINATO DE LISINA	
standards_concepts |> filter(
  str_detect(concept_name, "Arginine \\+ Lysine"))) |> union(
# "N05BA51" DIAZEPAM, COMBINACIONES CON	
standards_concepts |> filter(concept_class_id == "Ingredient",
  str_detect(concept_name, "^diazepam"))) |> union(
# "N05BA91" BENTAZEPAM
standards_concepts |> filter(concept_class_id == "Ingredient",
  str_detect(concept_name, "^BENTAZEPAM"))) |> union(
# "N05CM93" GLUTAMATO MAGNESICO BROMHIDRATO	
standards_concepts |> filter(concept_class_id == "Ingredient",
  str_detect(concept_name, "^magnesium glutamate"))) |> union(
# "N06BX54" DEANOL, COMBINACIONES CON	
standards_concepts |> filter(concept_class_id == "Ingredient",
  str_detect(concept_name, "^deanol"))) |> union(
# "N06BX95" GABOB EN COMBINACION	
standards_concepts |> filter(concept_class_id == "Substance",
  str_detect(concept_name, "^Gamma-aminobutyric acid"))) |> union(
# "R05CZ95" SULFONAMIDAS ASOCIADAS A MUCOLITICO Y/O EXPECTORANTE	
standards_concepts |> filter(concept_class_id == "Substance",
  str_detect(concept_name, "^Sulfonamide$"))) |> union(
# "R05DA91" DIHIDROCODEINA
standards_concepts |> filter(concept_class_id == "Ingredient",
  str_detect(concept_name, "^dihydrocodeine")))

```


```{r}
# mapped but with no relationship--------------------------------------------
gaia_clinical_drugs5 |> filter(atc_cod %in% c(
  "R05CB10", "R05DA20", "R05CA10", "R05FA02", "R01AX30"))
# For now 0. Is better use pres_farma_desc instead of atc_cod

```

```{r}
# manual atc drug_concept id relationship-------------------------------------
manual_atc_drug_relationship <- tibble(
  drug_concept_id = unmpaded_atc_codes_to_standard$concept_id,
  drug_source_concept_id = 0,
  drug_source_value = missing_atc_source_codes
)

```


```{r}
# obtain atc concepts relationships------------------------------------------
concepts_relationship_atc <- concepts_relationship |> 
  filter(relationship_id == "Maps to") |> 
  filter(concept_id_1 %in% atc_concept_codes)  |> 
  filter(concept_id_2 %in% standard_concept_codes) |> 
  left_join(atc_concepts |> 
              select(concept_code, concept_id_1 = concept_id)) |> 
  select(drug_concept_id = concept_id_2, 
         drug_source_concept_id = concept_id_1,
         drug_source_value = concept_code) |>
  # add manual relationships
  union(manual_atc_drug_relationship) |> 
  tidylog::distinct()

fwrite(concepts_relationship_atc, file.path("Target_tables", 
                  "AUXILIAR", "concepts_relationship_atc.csv"))

```


```{r}
# check one to many mappings-------------------------------------------------
list_of_concepts <- concepts_relationship |> 
  filter(relationship_id == "Maps to") |> 
  filter(concept_id_1 == 21601312) |> 
  pull(concept_id_2)

concepts_vocabulary |> filter(concept_id %in% list_of_concepts)

```

```{r}
# load siv_clinical_drugs----------------------------------------------------
siv_clinical_drugs2 <- fread(file.path("..", "Consign", "Resultados",
                               "gaia_masters", "siv_clinical_drugs2.csv"))

```


```{r}
# siv drug_concept_id mapping------------------------------------------------
concepts_relationship_siv_drug <- siv_clinical_drugs2 |> 
  left_join(standards_concepts |> select(cvx_concept_name = concept_name,
                                          concept_id)) |>
  mutate(drug_source_concept_id = 0) |> 
  select(drug_concept_id = concept_id,
         drug_source_concept_id,
         drug_source_value = tipo_vacuna) |> 
  distinct()
  
fwrite(concepts_relationship_siv_drug, file.path("Target_tables", 
                  "AUXILIAR", "concepts_relationship_siv_drug.csv"))

```

## From gaia to drug_exposure

```{r}
# populate table-------------------------------------------------------------
from_gaia_to_drug_exposure_0 <- gaia |>
  # temporal fix -> move to curation script
  filter(sip %in% sips_consign) |>
  # paste gaia_clinical_drugs5 vars
  select(-c(pres_farma_desc, 
            atc_cod, atc_desc,
            prin_act_cod, prin_act_desc,
            via_cod, via_desc)) |> 
  left_join(gaia_clinical_drugs5, by = "pres_farma_cod") |> 
  select(sip,
         receta_id,
         fecha_pres,
         fecha_disp,
         atc_cod,
         atc_desc,
         prin_act_cod,
         prin_act_desc,
         env_durac,
         pres_farma_desc,
         via_cod,
         via_desc,
         unidades,
         cadencia) |>
  transmute(
    person_source_value = sip,
    # drug_concept_id = "map",
    drug_exposure_start_date = if_else(!is.na(fecha_disp),
                                       fecha_disp, fecha_pres),
    drug_exposure_start_datetime = drug_exposure_start_date,
    drug_exposure_end_date = drug_exposure_start_date %m+% 
      days(min(1, ceiling(env_durac), na.rm = TRUE)),
    drug_exposure_end_datetime = drug_exposure_end_date,
    verbatim_end_date = NA_Date_,
    drug_type_concept_id = if_else(!is.na(fecha_disp),
                                       32825, 32838),
    stop_reason = NA_character_,
    refills = NA_integer_,
    quantity = 1,
    days_supply = ceiling(env_durac),
    sig =  glue("{unidades} form(s) each {cadencia} hours"),
    # route_concept_id = "map",
    lot_number = 0, # check if it is mandatory, else NA_integer
    provider_id = NA_integer_,
    visit_occurrence_id = NA_integer_,
    visit_detail_id = NA_integer_,
    drug_source_value = atc_cod,
    # drug_source_concept_id = "map",
    route_source_value = via_desc,
    dose_unit_source_value = NA_character_
            ) |> 
  left_join(person_ids, by = "person_source_value") |> 
  select(-person_source_value) 

```


```{r}
# mapping concept_ids--------------------------------------------------------
from_gaia_to_drug_exposure <- from_gaia_to_drug_exposure_0 |> 
  left_join(concepts_relationship_atc, 
            by = c("drug_source_value")) |>
  left_join(concepts_relationship_route,
            by = c("route_source_value")) |>
  mutate(drug_concept_id = if_else(is.na(drug_concept_id),
                                         0, drug_concept_id)) |> 
  mutate(drug_exposure_id = 1:n()) |> 
  relocate(
    drug_exposure_id,
    person_id,
    drug_concept_id,
    drug_exposure_start_date,
    drug_exposure_start_datetime,
    drug_exposure_end_date,
    drug_exposure_end_datetime,
    verbatim_end_date,
    drug_type_concept_id,
    stop_reason,
    refills,
    quantity,
    days_supply,
    sig,
    route_concept_id,
    lot_number,
    provider_id,
    visit_occurrence_id,
    visit_detail_id,
    drug_source_value,
    drug_source_concept_id,
    route_source_value,
    dose_unit_source_value
  ) 

```


```{r}
# write table----------------------------------------------------------------
fwrite(from_gaia_to_drug_exposure, append = FALSE,
       file = file.path("Target_tables", "AUXILIAR",
                        "from_gaia_to_drug_exposure.csv"))

from_gaia_to_drug_exposure <- fread(
  file.path("Target_tables", "AUXILIAR",
                        "from_gaia_to_drug_exposure.csv"))

last_gaia_drug_exposure_id <- 
  max(from_gaia_to_drug_exposure$drug_exposure_id)

# write table----------------------------------------------------------------
fwrite(from_gaia_to_drug_exposure, append = FALSE,
       file = file.path("Target_tables",
                        "drug_exposure_vid.csv"))

```

```{r}
# free up some memory--------------------------------------------------------
rm(gaia)

```

## From siv to drug exposure

```{r}
# populate table-------------------------------------------------------------
from_siv_to_drug_exposure_0 <- siv |>
  # temporal fix -> move to curation script
  filter(sip %in% sips_consign) |>
  select(sip,
         tipo_vacuna,
         nombre_vacuna,
         fecha_vacuna) |>
  transmute(
    person_source_value = sip,
    # drug_concept_id = "map",
    drug_exposure_start_date = fecha_vacuna,
    drug_exposure_start_datetime = fecha_vacuna,
    drug_exposure_end_date = fecha_vacuna,
    drug_exposure_end_datetime = fecha_vacuna,
    verbatim_end_date = NA_Date_,
    drug_type_concept_id = 32818,
    stop_reason = NA_character_,
    refills = 0,
    quantity = 1,
    days_supply = 0,
    sig =  NA_character_,
    route_concept_id = 4302612, # intramuscular
    lot_number = 0, # check if it is mandatory, else NA_integer
    provider_id = NA_integer_,
    visit_occurrence_id = NA_integer_,
    visit_detail_id = NA_integer_,
    drug_source_value = tipo_vacuna,
    # drug_source_concept_id = "map",
    route_source_value = "intramuscular",
    dose_unit_source_value = NA_character_
            ) |> 
  left_join(person_ids, by = "person_source_value") |> 
  select(-person_source_value) 

```


```{r}
# mapping concept_ids--------------------------------------------------------
from_siv_to_drug_exposure <- from_siv_to_drug_exposure_0 |> 
  left_join(concepts_relationship_siv_drug, 
            by = c("drug_source_value")) |>
  mutate(drug_exposure_id = 1:n() + last_gaia_drug_exposure_id) |> 
  relocate(
    drug_exposure_id,
    person_id,
    drug_concept_id,
    drug_exposure_start_date,
    drug_exposure_start_datetime,
    drug_exposure_end_date,
    drug_exposure_end_datetime,
    verbatim_end_date,
    drug_type_concept_id,
    stop_reason,
    refills,
    quantity,
    days_supply,
    sig,
    route_concept_id,
    lot_number,
    provider_id,
    visit_occurrence_id,
    visit_detail_id,
    drug_source_value,
    drug_source_concept_id,
    route_source_value,
    dose_unit_source_value
  )

```


```{r}
# write table----------------------------------------------------------------
fwrite(from_siv_to_drug_exposure, append = FALSE,
       file = file.path("Target_tables", "AUXILIAR",
                        "from_siv_to_drug_exposure.csv"))

# write table----------------------------------------------------------------
fwrite(from_siv_to_drug_exposure, append = TRUE,
       file = file.path("Target_tables",
                        "drug_exposure_vid.csv"))

```

# fact_relationship

## From mdr_to_fact_relationship

::: {callout-important}

This table cannot be populated because we don't have information about the sex of the children, and we cannot create a person entry for them. We have included this section in anticipation of the possibility of obtaining the sex of the newborns in the future.

:::

```{r}
#  From mdr_to_fact_relationship---------------------------------------------
# # mother to child
# from_mdr_to_fact_relationship_mother <- mdr |> 
#   distinct(sip_madre, sip_hijo) |> 
#   mutate(domain_concept_id_1 = "32879") |> 
#   mutate(domain_concept_id_2 = "32879") |> 
#   mutate(relationship_concept_id = "4248584") |> 
#   relocate(
#     domain_concept_id_1,
#     fact_id_1 = sip_madre,
#     domain_concept_id_2,
#     fact_id_2 = sip_hijo,
#     relationship_concept_id
#   )
#   
# # child to mother
# from_mdr_to_fact_relationship_child <- mdr |> 
#   distinct(sip_madre, sip_hijo) |> 
#   mutate(domain_concept_id_1 = "32879") |> 
#   mutate(domain_concept_id_2 = "32879") |> 
#   mutate(relationship_concept_id = "4285883") |> 
#   relocate(
#     domain_concept_id_1,
#     fact_id_1 = sip_hijo,
#     domain_concept_id_2,
#     fact_id_2 = sip_madre,
#     relationship_concept_id
#   )

```

```{r}
# union of mother to child and child to mother-------------------------------
# from_mdr_to_fact_relationship <- from_mdr_to_fact_relationship_mother |> 
#   union(from_mdr_to_fact_relationship_child)
# 
# # write table----------------------------------------------------------------
# # fwrite(from_mdr_to_fact_relationship, append = FALSE,
# #        file = file.path("Target_tables", "AUXILIAR",
# #                         "from_mdr_to_fact_relationship.csv"))
# # 
# # from_mdr_to_fact_relationship_write <- from_mdr_to_fact_relationship
# 
# # write table----------------------------------------------------------------
# fwrite(from_mdr_to_fact_relationship, append = FALSE,
#        file = file.path("Target_tables",
#                         "fact_relationship_vid.csv"))
  
```

# measurement

The target table **measurement** is populated with the information from the source table **REDMIVA**.

## From redmiva to measurement

When tipo_prueba is (PCR) in the source table, the concept id is ’586310: Measurement of Severe acute respiratory syndrome coronavirus 2 (SARS-CoV-2) Genetic material using Molecular method), while when is antigen tests is mapped to ‘37310257: Measurement of Severe acute respiratory syndrome coronavirus 2 antigen’.

```{r}
# PCR
concepts_vocabulary |> filter(concept_id == 586310)
# Antigen
concepts_vocabulary |> filter(concept_id == 37310257)
# positive
concepts_vocabulary |> filter(concept_id == 45884084)

```


```{r}
# populate table-------------------------------------------------------------
from_redmiva_to_measurement <- redmiva |> 
  # temporal fix -> move to curation script
  filter(sip %in% sips_consign) |>
  transmute(
    measurement_id = 1:n(),
    person_source_value = sip,
    measurement_concept_id = case_when(
      tipo_prueba == "PCR" ~ 586310,
      tipo_prueba == "AG" ~ 37310257,
      T ~ 0),
    measurement_date = fecha_prueba,
    measurement_datetime = fecha_prueba,
    measurement_time = fecha_prueba,
    measurement_type_concept_id = 32856,
    operator_concept_id = 0,
    value_as_number = 0,
    value_as_concept_id = 45884084,
    unit_concept_id = 0,
    range_low = 0,
    range_high = 0,
    provider_id = NA_integer_,
    visit_occurrence_id = NA_integer_,
    visit_detail_id = NA_integer_,
    measurement_source_value = 0,
    measurement_source_concept_id = 0,
    unit_source_value = 0,
    unit_source_concept_id = 0,
    value_source_value = resultado,
    measurement_event_id = NA_integer_,
    meas_event_field_concept_id = 0) |>
  left_join(person_ids, by = "person_source_value") |> 
  select(-person_source_value) |> 
  relocate(
    measurement_id, 
    person_id
    )
  
# write table----------------------------------------------------------------
fwrite(from_redmiva_to_measurement, append = FALSE,
       file = file.path("Target_tables",
                        "measurement_vid.csv"))

```

# cdm_source

```{r}
cdm_source <- tibble(
  cdm_source_name = "vid_consign",
  cdm_source_abbreviation = "vid_consign",
  cdm_holder = "FISABIO-HSRP",
  source_description = "Instance of the CONSIGN project utilizing the VID data",
  source_documentation_reference = "https://github.com/frasansa/OHDSI-VID_to_OMOP_ETL/tree/main/doc",
  cdm_etl_reference = "https://github.com/frasansa/OHDSI-VID_to_OMOP_ETL",
  source_release_date = ymd("2022-01-01"),
  cdm_release_date = ymd(Sys.Date()),
  cdm_version = "5.4",
  cdm_version_concept_id = 756265,
  vocabulary_version = "v5.0 31-MAY-23"
    )

# write table----------------------------------------------------------------
fwrite(cdm_source, append = FALSE,
       file = file.path("Target_tables",
                        "cdm_source_vid.csv"))

```


::: {.tocify-extend-page data-unique="tocify-extend-page" style="height: 0;"}
:::



